\section{Pre-Communion Prayers}

\subsection{Psalm 22}

The Lord is my shepherd; therefore can I lack nothing. He maketh me to lie down in a green pasture; He leadeth me beside the still water. He hath converted my soul; He hath set me on the paths of righteousness, for His Name’s sake. Yea, though I walk through the valley of the shadow of death, I will fear no evil, for Thou art with me; Thy rod and Thy staff, they have comforted me. Thou hast prepared a table before me against them that trouble me; Thou hast anointed my head with oil, and Thy cup that inebriateth me, how strong it is! And Thy mercy shall follow me all the days of my life, and I will dwell in the house of the Lord unto length of days.

\subsection{Psalm 23}

The earth is the Lord’s, and the fullness thereof; the compass of the world, and all that dwell therein. He hath founded it upon the seas, and prepared it upon the floods. Who shall ascend into the hill of the Lord, or who shall stand in His holy place? Even he that hath clean hands, and a pure heart, who doth not take his soul in vain, nor swear falsely to his neighbor. He shall receive a blessing from the Lord, and mercy from God his Savior. This is the generation of them that seek the Lord, even of them that seek the face of the God of Jacob. Lift up your gates, O ye princes, and be ye lift up, ye everlasting doors, and the King of glory shall come in. Who is this King of glory? It is the Lord strong and mighty, even the Lord mighty in battle. Lift up your gates, O ye princes, and be ye lift up, ye everlasting doors, and the King of glory shall come in. Who is this King of glory? Even the Lord of hosts, He is the King of glory.

\subsection{Psalm 115}

I believed, so I spake; but I was greatly humbled. I said in my confusion, All men are liars. What shall I render unto the Lord, for all that He hath rendered unto me? I will take the cup of salvation, and call upon the Name of the Lord. I will pay my vows unto the Lord in the presence of all His people. Precious in the sight of the Lord is the death of His saints. O Lord, I am Thy servant; I am Thy servant, and the son of Thine handmaid; Thou hast broken my bonds in sunder. I will offer unto Thee a sacrifice of thanksgiving, and will call upon the Name of the Lord. I will pay my vows unto the Lord in the presence of all His people, in the courts of the Lord’s house, even in the midst of thee, O Jerusalem.

\subsection{A Prayer of St. Basil the Great}

    O Lord and Master, Jesus Christ, our God, Fountain of life and immortality, Creator of all things visible and invisible; Consubstantial and Co-eternal Son of the eternal Father, who in thine exceeding great love didst become incarnate in the latter days, and was crucified for us ungrateful and wicked children, and by thine own Blood didst renew our nature corrupted by sin: Do thou, O Immortal King, receive me, a repentant sinner; incline thine ear unto me and hear my prayer. I have sinned, O Lord, I have sinned against heaven and before thee, and I am not worthy to lift up my eyes to the majesty of thy glory, for I have affronted thy goodness, and broken thy commandments, and disobeyed thy laws. But thou, O Lord, most loving, longsuffering and merciful, hast not given me over to perish in my sin, but dost ever await my return. For, O Thou who lovest mankind, thou hast said, by thy Prophet, that thou hast no pleasure in the death of a sinner, but rather than he should turn from his wickedness and live. Thou dost not desire, O Master, to destroy the works of thy hands or that they should perish, but willest that all men should be saved and come to the knowledge of the Truth. Wherefore I, although unworthy both of heaven and of earth and of this temporary life, even I, a wretched sinner who had given myself over to every evil desire, despair not of salvation, though I have been wholly subject to sin, a slave to passion, and have defiled thine image within me, who am thy creation and thy work; but trusting in thine infinite compassion, draw nigh unto thee. Receive me, O Lord, thou that lovest mankind, as thou didst receive the sinful woman, the thief, the publican and the prodigal son. Take away the heavy burden of my sins, O Thou that takest away the sins of the world, and healest the infirmities of men, and callest all that are weary and heavy laden to thyself and givest them rest; thou that camest not to call the righteous but sinners to repentance, cleanse thou me from all stain of body and soul and teach me to fulfill holiness in thy fear, that with the witness of my conscience pure, I may receive a portion of thy Holy Gifts, and be united to thy Holy Body and Precious Blood, and may have thee, with thy Father and Holy Spirit, dwelling and abiding in me. And grant, O Lord Jesus Christ, my God, that the partaking of thy precious and Life-giving Mysteries may not be to my condemnation, nor may not through the weakness of my soul and body be received unworthily; but grant that, even unto my last breath, I may partake of a portion of thy Holy Gifts without condemnation, unto the Communion of thy Holy Spirit, as a preparation for eternal Life and for a good defense at thy dread Judgment Seat; so that I, together with all thine elect, may also receive those incorruptible good things which thou hast prepared for them that love thee, O Lord; in whom thou art glorified forever. Amen.

\subsection{Another Prayer of St. Basil the Great}

    O Lord, I know that I am unworthy to receive thy Holy Body and Precious Blood; I know that I am guilty, and that I eat and drink condemnation to myself, not discerning the Body and Blood of Christ my God. But trusting in thy loving-kindness I come unto thee who has said: He that eateth my Body and drinketh my Blood shall dwell in me and I in him. Therefore, O Lord, have compassion on me and make not an example of me, thy sinful servant. But do unto me according to thy great mercy, and grant that these Holy Gifts may be for me unto the healing, purification, enlightenment, protection, salvation and sanctification of my soul and body, and to the expulsion of every evil imagination, sinful deed or work of the Devil. May they move me to reliance on thee and to love thee always, to amend and keep firm my life; and be ever in me to the increase of virtue, to the keeping of thy Commandments, to the communion of the Holy Spirit, and as a good defense before thy dread Judgment Seat, and for Life Eternal. Amen.

\subsection{A Prayer of St. John Chrysostom}

    O Lord my God, I know that I am not worthy nor sufficient that thou shouldest enter under my roof into the habitation of my soul, for it is all deserted and in ruins, and thou hast not a fitting place in me to lay thy head. But as from the heights of thy glory thou didst humble thyself, so now bear me in my humility; as thou didst deign to lie in a manger in a cave, so deign now also to come into the manger of my mute soul and corrupt body. As thou didst not refrain from entering into the house of Simon the leper, or shrink from eating there with sinners, so also vouchsafe to enter the house of my poor soul, all leprous and full of sin. Thou didst not reject the sinful woman who ventured to draw near to touch thee, so also have pity on me, a sinner, approaching to touch thee. And grant that I may partake of thine All-holy Body and Precious Blood for the sanctification, enlightenment and strengthening of my weak soul and body; for the relief from the burden of my many sins; for my preservation against all the snares of the devil; for victory over all my sinful and evil habits; for the mortification of my passions; for obedience to thy Commandments; for growth in thy divine Grace and for the inheritance of thy Kingdom. For it is not with careless heart that I approach thee, O Christ my God, but I come trusting in thine infinite goodness, and fearing lest I may be drawn afar from thee and become the prey of the wolf of souls. Wherefore, I pray thee, O Master, who alone art holy, that thou wouldest sanctify my soul and body, my mind and heart and reins, and renew me entirely. Implant in my members the fear of thee, be thou my helper and guide, directing my life in the paths of peace, and make me worthy to stand at thy right hand with thy Saints; through the prayers and intercessions of thine immaculate Mother, of thy Bodiless Servitors, of the immaculate Powers, and of all the Saints who from all ages have been well-pleasing unto thee. Amen.

\subsection{A Prayer of St. John of Damascus}

    O Lord and Master Jesus Christ, our God, who alone hath power to forgive the sins of men, do thou, O Good One who lovest mankind, forgive all the sins that I have committed in knowledge or in ignorance, and make me worthy to receive without condemnation thy divine, glorious, immaculate and life-giving Mysteries; not unto punishment or unto increase of sin; but unto purification, and sanctification and a promise of thy Kingdom and the Life to come; as a protection and a help to overthrow the adversaries, and to blot out my many sins. For thou art a God of mercy and compassion and love toward mankind, and unto Thee we ascribe glory, together with the Father and the Holy Spirit: now and ever, and unto ages of ages. Amen.

\subsection{Another Prayer of St. John of Damascus}

    I stand before the gates of thy Temple, and yet I refrain not from my evil thoughts. But do thou, O Christ my God, who didst justify the publican, and hadst mercy on the Canaanite woman, and opened the gates of Paradise to the thief; open unto me the compassion of thy love toward mankind, and receive me as I approach and touch thee, like the sinful woman and the woman with the issue of blood; for the one, by embracing thy feet received the forgiveness of her sins, and the other by but touching the hem of thy garment was healed. And I, most sinful, dare to partake of thy whole Body. Let me not be consumed, but receive me as thou didst receive them, and enlighten the perceptions of my soul, consuming the accusations of my sins: through the intercessions of Her that, without stain, gave Thee birth, and of the heavenly Powers: for thou art blessed unto ages of ages. Amen.

\subsection{A Prayer of St. John Chrysostom}

    I believe, O Lord, and I confess that thou art truly the Christ, the Son of the living God, who didst come into the world to save sinners, of whom I am chief. And I believe that this is truly thine own precious Body, and that this is truly thine own precious Blood. Wherefore I pray thee, have mercy upon me and forgive my transgressions both voluntary and involuntary, of word and of deed, of knowledge and of ignorance; and make me worthy to partake without condemnation of thine immaculate Mysteries, unto remission of my sins and unto life everlasting. Amen.

    Of thy Mystic Supper, O Son of God, accept me today as a communicant: for I will not speak of thy Mystery to thine enemies, neither will I give thee a kiss as did Judas; but like the thief will I confess thee: Remember me, O Lord, in thy Kingdom.

    Not unto judgment nor unto condemnation be my partaking of thy Holy Mysteries, O Lord, but unto the healing of soul and body.

\cleardoublepage

\section{Post-Communion Prayers}

    Glory to thee, O God; Glory to thee, O God; Glory to thee, O God.

\subsection{A Prayer (Anonymous)}

    I thank thee, O Lord my God, that thou hast not rejected me, a sinner, but hast accounted me worthy to become a communicant of thy holy Mysteries. I thank thee that thou hast accounted me, the unworthy, worthy to partake of thine immaculate and heavenly gifts. But, O Master who lovest mankind, who didst both die for us and rise again, and didst bestow upon us these thy terrible and life-giving Mysteries for the benefiting and sanctification of our souls and bodies; grant that they may be for me also unto the healing of soul and body, unto the averting of everything contrary thereto; unto the enlightenment of the eyes of my heart; unto the peace of my spiritual powers; unto faith invincible; unto love unfeigned; unto fulfilling of wisdom; unto the keeping of thy commandments; unto growth in thy divine grace, and the attainment of thy kingdom; that by them preserved in thy holiness, I may ever remember thy grace, and henceforth live not unto myself, but unto thee, our Master and Benefactor. And thus, when this life is ended in the hope of eternal life, I may attain unto everlasting rest, where the voice of those who keep festival is unceasing, and the delight of those who behold the ineffable beautify of thy countenance is boundless: for thou art the true desire and unutterable joy of those who love thee, O Christ our God, and all creation hymneth thee forever. Amen.
    
\subsection{Another Prayer (Anonymous)}

    May thy holy Body, O Lord Jesus Christ our God, be unto me for life eternal, and thy precious Blood unto remission of my sins. May this Eucharist be unto me for joy, health, and gladness; and at thy dread Second Coming make me, a sinner, worthy to stand at the right hand of thy glory: through the intercessions of thine all-immaculate Mother and of all thy Saints.  Amen.

\subsection{A Prayer of St. Basil the Great}

    O Master, Christ our God, King of the ages, and maker of all things: I thank thee for all the good things which thou hast bestowed upon me, and for this partaking of thine immaculate and life-giving Mysteries. Wherefore I pray thee, who art good and lovest mankind: Keep me under thy protection, and in the shadow of thy wings; and grant unto me with a pure conscience and even unto my last breath, to partake of thy holy Mysteries, unto remission of sins and unto life everlasting. For thou art the Bread of Life, the Fountain of holiness, the Giver of good things, and unto thee we ascribe glory: to the Father, and to the Son, and to the Holy Spirit: now and ever, and unto ages of ages.  Amen.

\subsection{A Prayer of St. Simon Metaphrastes}

    O thou who willingly dost give thy flesh to me as food,\\
    Thou who art a Fire, consuming the unworthy,\\
    Consume me not, O my Creator;\\
    But rather pass through all my body parts,\\
    Into all my joints, my reins, my heart.\\
    Burn thou the thorns of all my transgressions,\\
    Cleanse my soul, and hallow thou my thoughts.\\
    Make firm my knees, and my bones likewise;\\
    Enlighten as one my five senses,\\
    Establish me wholly in thy fear;\\
    Ever shelter me, and guard and keep me\\
    From every soul-corrupting deed and word,\\
    Chasten me, purify me, and control me;\\
    Adorn me, teach me, and enlighten me.\\
    Show me to be a Tabernacle of thy Spirit only,\\
    And in no wise the dwelling-place of sin,\\
    That from me, thy habitation, \\
    \hspace*{2em} through the entrance of thy Communion,\\
    Every evil deed and every passion may flee as from fire.\\
    As intercessors I bring to thee all the Saints,\\
    Both the Angelic Leaders of the Bodiless Powers,\\
    Thy Fore-runner, and thy wise Apostles;\\
    And besides these, thine immaculate and chaste Mother;\\
    Do thou accept their prayers, my Christ, \\
    \hspace*{2em} who art compassionate,\\
    And make thy servant to be a child of the light:\\
    For thou alone, Good Lord, are the sanctification\\
    \hspace*{2em} and splendor of our souls,\\
    And to thee as God and Master, day by day,\\
    Duly we ascribe all glory.

\subsection{A Prayer to the All-Holy Theotokos (Anonymous)}

    O  All-holy Lady Theotokos, light of my darkened soul, my hope, my shelter, my refuge, my consolation and my joy: I thank thee that thou hast accounted me worthy, although unworthy, to be a partaker of the immaculate Body and precious Blood of thy Son. But do thou, who gavest birth to the true Light, enlighten the mental eyes of my heart; O thou who didst bear the fountain of immortality, quicken thou me who lie dead in sin, O compassion-loving Mother of the merciful God, have mercy upon me, and grant me humility and contrition of heart, and meekness in my thoughts, and deliverance from the bondage of my vain imaginings. And account me worthy, even unto my last breath, to receive without condemnation the sanctification of the immaculate Mysteries, unto the healing of both soul and body. And grant unto me tears of repentance and confession, that I may hymn thee and glorify thee all the days of my life: for blessed and glorified art thou unto all ages.  Amen.


\cleardoublepage
