\section{Litanies}

\subsection{The Litany of Peace}

In peace, let us pray to the Lord.

For the peace from above and the salvation of our souls, let us pray to the Lord.

For the peace of the whole world, the good estate of the holy churches of God and the union of all men, let us pray to the Lord.

For this holy house and those who with faith, reverence, and fear of God enter therein, let us pray to the Lord.

For our metropolitan, \rubric{(name)}, our bishop, \rubric{(name)}, the honorable presbytery; the diaconate in Christ, all the clergy and the people, let us pray to the Lord.

For our president, civil authorities, and armed forces, let us pray to the Lord.

For this city \rubric{(or \unrubric{countryside} or \unrubric{village})} and every city and countryside and the faithful who dwell therein, let us pray to the Lord.

For healthful seasons, abundance of the fruits of the earth and peaceful times, let us pray to the Lord.

For travelers by sea, by land, and by air, the sick, the suffering, the captive, and for their salvation, let us pray to the Lord.

For our deliverance from all tribulation, wrath, danger, and necessity, let us pray to the Lord.

Help us; save us; have mercy on us; and keep us, O God, by thy grace.

Calling to remembrance our all-holy, immaculate, most blessed and glorious Lady the Theotokos and ever-virgin Mary, with all the saints, let us commend ourselves and each other and all our life unto Christ our God.

For unto thee are due all glory, honor, and worship to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\subsection{The Litany of Supplication}

Let us complete our prayer prayer unto the Lord.

Help us; save us; have mercy on us; and keep us, O God, by thy grace.

That the whole day \rubric{(or \unrubric{evening})} may be perfect, holy, peaceful, and sinless, let us ask of the Lord.

An angel of peace, a faithful guide, a guardian of our souls and bodies, let us ask of the Lord.

Pardon and forgiveness of our sins and transgressions, let us ask of the Lord.

All things good and profitable for our souls and peace for the world, let us ask of the Lord.

That we may complete the remaining time of our life in peace and repentance, let us ask of the Lord.

A Christian ending to our life, painless, blameless, peaceful, and a good defense before the fearful judgment seat of Christ, let us ask.

Calling to remembrance our all-holy, immaculate, most blessed and glorious Lady the Theotokos and ever-virgin Mary, with all the saints, let us commend ourselves and each other and all our life unto Christ our God.

For thou art a good God and lovest mankind, and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\subsection{The Litany of Fervent Supplication}

Let us say with our whole soul, and with our whole mind, let us say.

O Lord Almighty, the God of our Fathers, we pray Thee, hearken and have mercy.

Have mercy on us, O God, according to Thy great mercy, we pray Thee, hearken and have mercy.

Again we pray for all pious and Orthodox Christians.

Again we pray for our father and Metropolitan \rubric{(name)}, \rubric{(\unrubric{and for our Bishop} (name))}.

Again we pray for our brethren: the priests, hieromonks, deacons, hierodeacons and monastics and all our brotherhood in Christ.

Again we pray for mercy, life, peace, health, salvation and visitation and pardon and remission of sins for \rubric{(\unrubric{the servants of God,} (names)\unrubric{, and})} all Orthodox Christians of true worship, who live and dwell in this community.

Again we pray for the blessed and ever-memorable founders of this holy church and for \rubric{(\unrubric{the departed servants of God,} (names)\unrubric{, and})} all our fathers and brethren, the Orthodox departed this life before us, who here and in all the world lie asleep in the Lord.

Again we pray for those who bear fruit and do good works in this holy and all-venerable temple, those who serve and those who sing, and for all the people here present, who await Thy great and rich mercy.
 
O Lord our God, receive this fervent supplication of Thy servants, and have mercy on us according to the multitude of Thy mercy, and send down Thy compassions upon us and upon all Thy people, who await Thy great and rich mercy.

For Thou art a merciful God and lovest mankind, and unto Thee we ascribe glory: to the Father, and to the Son, and to the Holy Spirit; now and ever, and unto ages of ages. Amen.

\subsection{The Litany for the Catechumens}

Pray to the Lord, ye catechumens.

Let us the faithful, pray for the catechumens, that the Lord will have mercy on them.

That He will teach them the word of truth.

That He will reveal to them the gospel of righteousness.

That He will unite them to His holy, catholic and apostolic Church.

Help them; save them; have mercy on them; and keep them, O God, by Thy grace.

Bow your heads to the Lord, ye catechumens.

O God, our God, the Creator and Maker of all things, Who willest that all men should be saved and should come unto the knowledge of the truth: Look down upon Thy servants the catechumens, and deliver them from the ancient delusion and from the wiles of the adversary. And call them unto life eternal, illuminating their souls and bodies and numbering them with Thy rational flock, which is called by Thy Holy Name.

That with us they may glorify Thine all-honorable and majestic Name: of the Father, and of the Son, and of the Holy Spirit; now and ever, and unto ages of ages. Amen.

\subsection{The Litany for those Preparing for Illumination}

Pray unto the Lord, ye who are preparing for Illumination.

Ye faithful, pray unto the Lord for these brethren who are preparing for Holy Illumination and for their salvation.

That the Lord God will establish them and strengthen them.

That He will illuminate them with the light of wisdom and of piety.

That He will grant unto them, in His own good time, the laver of regeneration, the remission of sins, and the garment of incorruption.

That He will beget them with water and the Spirit.

That He will grant unto them the perfection of faith. 

That He will number them with His holy and chosen flock.

Help them; save them; have mercy on them; and keep them, O God, by Thy grace.

Bow your heads to the Lord, ye who are preparing for Illumination.

Show the light of Thy countenance, O God, upon those who are preparing for Holy Illumination, and who desire to put away the defilement of sin. Enlighten their understanding. Establish them in the Faith. Strengthen them in hope. Perfect them in love. Make them honorable members of Thy Christ, Who gave Himself for our souls.

For Thou art our Illumination, and unto Thee do we ascribe glory: to the Father, and to the Son, and to the Holy Spirit; now and ever, and unto ages of ages. Amen.
