\section{Prayers at the Table}

\subsection{Before Meals}

In the Name of the Father, and of the Son, and of the Holy Spirit. Amen.

Our Father, who art in heaven, hallowed be thy Name; thy kingdom come; thy will be done on earth, as it is in heaven. Give us this day our daily bread; and forgive us our trespasses, as we forgive those who trespass against us; and lead us not into temptation, but deliver us from evil.

For thine is the kingdom, and the power, and the glory, of the Father, and of the Son, and of the Holy Spirit: now and ever, and unto ages of ages. Amen.

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Lord, have mercy. \rubric{(thrice)}

\rubric{Then}

    O Christ our God, bless the food and drink of thy servants, for thou art Holy always; now and ever, and unto ages of ages. Amen.

\rubric{Or}

    They that hunger shall eat and be satisfied, they that seek after the Lord shall praise him; their hearts shall live forever. Amen.

\rubric{Or}

    Bless us, O Lord, and these thy gifts of which we are about to partake, for thou art blessed and glorified; now and ever, and unto ages of ages. Amen.

\subsection{After Meals}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Lord, have mercy. \rubric{(thrice)}

\rubric{Then}

    Blessed is God, who is merciful unto us and nourisheth us from His bounteous gifts by His Grace and compassion, always, now and ever, and unto ages of ages. Amen.

\rubric{Or}

    We thank thee, O Christ our God, that thou hast satisfied us with thy earthly gifts, deprive us not of thy Heavenly Kingdom; but as thou entered into the midst of thy disciples, O Savior, and gave them peace, enter also among us and save us. Amen.

\rubric{Or}

    We thank thee, O God, the Giver of all good things, for these gifts and all thy mercies, and we bless thy Holy Name, always, now and ever, and unto ages of ages. Amen.

\cleardoublepage
