\section{Simplified Midnight Office}

In the Name of the Father, and of the Son, and of the Holy Spirit. Amen.

Glory to thee, our God, glory to thee.

O heavenly King, O Comforter, the Spirit of truth, who art in all places and fillest all things; Treasury of good things and Giver of life: Come and dwell in us and cleanse us from every stain, and save our souls, O gracious Lord.

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever and unto ages of ages. Amen.

O come, let us worship and fall down before God our King. \rubric{(metania)}

O come, let us worship and fall down before Christ our King and our God. \rubric{(metania)}

O come, let us worship and fall down before Christ Himself, our King and our God. \rubric{(metania)}

\subsection{Psalm 50}

Have mercy upon me, O God, according to thy great mercy: according to the multitude of thy tender mercies blot out mine iniquity. Wash me thoroughly from mine iniquity, and cleanse me from my sin. For I acknowledge mine iniquity, and my sin is ever before me. Against thee only have I sinned, and done evil in thy sight: that thou mightest be justified in thy words, and prevail when thou art judged. For behold, I was shapened in iniquity, and in sins did my mother conceive me.  For behold, thou hast loved truth: the unclear and hidden things of thy wisdom thou hast made clear to me. Thou shalt sprinkle me with hyssop, and I shall be clean; thou shalt wash me, and I shall be whiter than snow. Thou shalt make me to hear joy and gladness; the bones which thou hast broken shall rejoice. Turn away thy face from my sins, and blot out all mine iniquities. Create in me a clean heart, O God, and renew a right spirit within me. Cast me not away from thy presence, and take not thy Holy Spirit from me. Restore unto me the joy of thy salvation, and steady me with a guiding spirit.  Then will I teach transgressors thy ways, and the impious shall be converted unto thee. Deliver me from bloodguiltiness, O God, thou God of my salvation, and my tongue shall sing aloud of thy righteousness. O Lord, open thou my lips, and my mouth shall declare thy praise. For hadst thou desired sacrifice, I would have given it thee; thou delightest not in burnt offerings. Sacrifices to God are a contrite spirit: a contrite and humble heart, O God, thou wilt not despise. Do good, O Lord, in thy good will unto Zion, that the walls of Jerusalem may be built up. Then shalt thou be pleased with the sacrifice of righteousness, with burnt offering and whole burnt offerings; Then shall they offer bullocks upon thine altar.

\subsection{Psalm 120}

I lifted up mine eyes unto the hills; from whence will my help come? My help cometh even from the Lord, Who hath made heaven and earth. Suffer not thy feet to slip, nor Him that keepeth thee to slumber. Behold, He that keepeth Israel shall neither slumber nor sleep. The Lord Himself shall keep thee; the Lord is thy shelter upon thy right hand; The sun shall not burn thee by day, neither the moon by night. The Lord shall keep thee from all evil; yea, the Lord shall preserve thy soul. The Lord shall preserve thy going out, and thy coming in, from this time forth, and for evermore.

\subsection{Psalm 133}

Behold now, bless ye the Lord, all ye servants of the Lord, that stand in the house of the Lord, even in the courts of the house of our God. Lift up your hands by night in the sanctuary, and bless the Lord. The Lord bless thee out of Zion, Who hath made heaven and earth.

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Alleluia, alleluia, alleluia. Glory to thee, O God. \rubric{(thrice)}

Lord, have mercy. \rubric{(thrice)}

\subsection{Troparia to the Holy Trinity}

Having arisen from sleep, we fall down before thee, O Blessed One, and sing to thee, O Mighty One, the Angelic Hymn: Holy, holy, holy art thou, O God. Through the Theotokos have mercy on us.

Glory to the Father, and to the Son, and to the Holy Spirit:

From my bed and sleep Thou hast raised me: O Lord, enlighten my mind and my heart, and open my lips that I may praise thee, O Holy Trinity: Holy, holy, holy art thou, O God. Through the Theotokos have mercy on us.

Both now and ever, and unto ages of ages. Amen.

Suddenly the Judge shall come, and the deeds of each shall be revealed: but with fear we cry out in the middle of the night: Holy, holy, holy art thou, O God. Through the Theotokos have mercy on us.

\subsection{Prayer to the Holy Trinity}

Arising from sleep I thank thee, O holy Trinity, because of the abundance of thy goodness and longsuffering thou wast not wroth with me, slothful and sinful as I am; neither hast thou destroyed me in my transgressions: but in thy compassion raised me up, as I lay in despair; that at dawn I might sing the glories of thy Majesty. Do thou now enlighten the eyes of my understanding, open my mouth to receive thy words, teach me thy commandments, help me to do thy will, confessing thee from my heart, singing and praising thine All-holy Name: of the Father, and of the Son, and of the Holy Spirit: now and ever, and unto ages of ages. Amen.

\subsection{The Creed}

I believe in one God, the Father Almighty, Maker of heaven and earth, and of all things visible and invisible;

And in one Lord Jesus Christ, the Son of God, the Only-begotten, Begotten of the Father before all worlds, Light of Light, Very God of Very God, Begotten, not made; of one essence with the Father, by whom all things were made:

Who for us men and for our salvation came down from heaven, and was incarnate of the Holy Spirit and the Virgin Mary, and was made man;

And was crucified also for us under Pontius Pilate, and suffered and was buried;

And the third day He rose again, according to the Scriptures;

And ascended into heaven, and sitteth at the right hand of the Father;

And He shall come again with glory to judge the quick and the dead, Whose kingdom shall have no end.

And I believe in the Holy Spirit, the Lord, and Giver of Life, Who proceedeth from the Father, Who with the Father and the Son together is worshiped and glorified, Who spake by the Prophets;

And I believe in One Holy Catholic and Apostolic Church.

I acknowledge one Baptism for the remission of sins.

I look for the Resurrection of the dead.

And the Life of the world to come. Amen.

\subsection{A Prayer of St. Basil}

We bless thee, O God most high and Lord of mercies, who ever workest great and mysterious deeds for us, glorious, wonderful, and numberless; who providest us with sleep as a rest from our infirmities and as a repose for our bodies tired by labor. We thank thee that thou hast not destroyed us in our transgressions, but in thy love toward mankind thou hast raised us up, as we lay in despair, that we may glorify thy Majesty. We entreat thine infinite goodness, enlighten the eyes of our understanding and raise up our minds from the heavy sleep of indolence; open our mouths and fill them with thy praise, that we may unceasingly sing and confess thee, who art God glorified in all and by all, the eternal Father, the Only-Begotten Son, and the all-holy and good and life-giving Spirit: now and ever, and unto ages of ages. Amen.
%\enlargethispage{-2\baselineskip} % Widow prevention

O most glorious, ever-virgin, blessed Theotokos, present our prayer to thy Son our God, and intercede with him that through thee he may save our souls.

The Father is my Hope; \rubric{(metania)}\\
The Son is my Refuge; \rubric{(metania)}\\
The Holy Spirit is my Protection; \rubric{(metania)}\\
O Holy Trinity: Glory to thee.

In thee, O Mother of God, I place all my hope; keep me under thy protection.

It is truly meet to bless thee, O Theotokos, ever blessed and all-blameless, and the mother of our God. More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

O Lord who lovest mankind, forgive those who hate and wrong us. Do good to those who do good. Grant our brethren and kindred their petitions leading unto salvation and eternal life. Visit the sick and grant them healing. Guide those at sea. Journey with those who travel. Struggle alongside the Orthodox. To those who serve and are kind to us, grant remission of sins.

On Thy servants \rubric{(names of the living)}, and on those who have charged us, unworthy as we are, to pray for them, have mercy according to Thy great mercy. Remember, O Lord, Thy servants \rubric{(names of the departed)}, our fathers and brethren who have fallen asleep, and grant them rest where the light of Thy countenance shines. Remember, O Lord, those who bear fruit and do good works in Thy holy churches and grant them their petitions leading unto salvation and eternal life. Remember also, O Lord, us, Thy humble, sinful and unworthy servants, and enlighten our minds with the light of Thy knowledge, and guide us in the way of Thy commandments, by the prayers of our immaculate Lady, the Theotokos, and Ever-Virgin Mary, and of all Thy Saints, for Thou art blessed to the ages of ages. Amen. 

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian.}

O Lord and Master of my life, take from me the spirit of sloth, meddling, lust of power and idle talk. \rubric{(prostration)}

But give rather the spirit of chastity, humility, patience, and love to thy servant. \rubric{(prostration)}

Yea, O Lord and King, grant me to see my own sins and not to judge my brother, for thou art blessed unto ages of ages. Amen. \rubric{(prostration)}

\rubric{Lastly, we say:}

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
