\section{Ninth Hour}

In the Name of the Father, and of the Son, and of the Holy Spirit. Amen.

Glory to thee, our God, glory to thee.

O heavenly King, O Comforter, the Spirit of truth, who art in all places and fillest all things; Treasury of good things and Giver of life: Come and dwell in us and cleanse us from every stain, and save our souls, O gracious Lord.

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever and unto ages of ages. Amen.

O come, let us worship and fall down before God our King. \rubric{(metania)}

O come, let us worship and fall down before Christ our King and our God. \rubric{(metania)}

O come, let us worship and fall down before Christ Himself, our King and our God. \rubric{(metania)}

\subsection{Psalm 83}

How amiable are Thy dwellings, O Lord of hosts! My soul desireth and longeth for the courts of the Lord; my heart and my flesh have rejoiced in the living God. Yea, the sparrow hath found her an house, and the dove a nest where she may lay her young, even Thy altars, O Lord of hosts, my King and my God. Blessed are they that dwell in Thy house, for ever and ever will they praise Thee. Blessed is the man whose help is from Thee, in his heart he hath proposed ascents into the valley of tears, unto the place which he hath appointed, for the law-giver shall give the blessing. They will go from strength to strength; the God of gods shall appear in Zion. O Lord God of hosts, hear my prayer; hearken, O God of Jacob. Behold, O God, our defender, and look upon the face of Thy Christ. For one day in Thy courts is better than a thousand; I have preferred to be a doorkeeper in the house of my God, than to dwell in the tents of sinners. For the Lord loveth mercy and truth, God will give grace and glory; the Lord shall withhold no good thing from them that walk innocently. O Lord God of hosts, blessed is the man that putteth his trust in Thee.

\subsection{Psalm 84}

Thou hast been gracious, O Lord, unto Thy land, Thou hast turned back the captivity of Jacob. Thou hast forgiven the offenses of Thy people; Thou hast covered all their sins. Thou hast curtailed all Thy displeasure; Thou hast relented from the wrath of Thine indignation. Convert us, then, O God of our salvation, and let Thine anger cease from us. Wilt Thou be displeased at us for ever? Or wilt Thou stretch out Thy wrath from one generation to another? O God, Thou shalt stay Thyself; Thou shalt revive us, and Thy people shall rejoice in Thee. Show us, O Lord, Thy mercy, and grant us Thy salvation. I will hear what the Lord God will say concerning me; for He shall speak peace unto His people, and to His saints, and to them that turn their hearts unto Him. Surely His salvation is nigh them that fear Him, that glory may dwell in our land. Mercy and truth are met together, justice and peace have kissed each other. Truth hath flourished out of the earth, and justice hath looked down from heaven. For the Lord shall show loving-kindness, and our land shall give her increase. Justice shall go before Him, and shall set His steps in the way.

\subsection{Psalm 85}

Bow down Thine ear, O Lord, and hear me, for I am poor and in misery. Preserve Thou my soul, for I am holy; save Thy servant, O my God, that putteth his trust in Thee. Have mercy upon me, O Lord, for I will call upon Thee all day. Give joy to the soul of Thy servant, for unto Thee have I lifted up my soul. For Thou, Lord, art good and gentle, and of great mercy unto all them that call upon Thee. Give ear, Lord, unto my prayer, and heed the voice of my supplication. In the day of my trouble I called upon Thee, for Thou hast heard me. Among the gods there is none like unto Thee, O Lord, nor are there any deeds according unto Thy deeds. All nations whom Thou hast made shall come and bow down before Thee, O Lord, and shall glorify Thy Name. For Thou art great, and doest wondrous things; Thou art God alone. Guide me, O Lord, in Thy way, and I will walk in Thy truth; O let my heart rejoice to fear Thy Name. I will thank Thee, O Lord my God, with all my heart, and I will praise Thy Name for evermore. For great is Thy mercy toward me, and Thou hast delivered my soul from the nethermost hell. O God, the wicked are risen against me, and the congregations of the mighty have sought after my soul, and have not set Thee before them. But Thou, O Lord my God, art compassionate and merciful, longsuffering, and greatly charitable and true. O look upon me, and have mercy upon me, give Thy strength unto Thy servant, and help the son of Thine handmaid. Work some sign upon me for good, that they who hate me may see, and be ashamed, because Thou, Lord, hast holpen me, and comforted me.

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Alleluia, alleluia, alleluia. Glory to thee, O God. \rubric{(thrice)}

Lord, have mercy. \rubric{(thrice)}

\subsection{Troparia and Verses}

\rubric{If it is a weekday of Great Lent, the following troparia and verses are sung in Tone 8, else we say \unrubric{Glory...}, the troparion of the day, then \unrubric{Both now...}. The troparion of the day can be found starting on page \pageref{weekday}.}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

O thou, who at the ninth hour, for our sake didst taste death in the flesh: Mortify thou the pride of our flesh, and save us, O Christ God. \rubric{(prostration)}

\rubric{Verse 1:} Let my supplication draw nigh before thee, O Lord; according to thine oracle give me understanding. \rubric{(prostration)}

\rubric{Verse 2:} Let my petition come before thee, O Lord: according to thine oracle deliver me. \rubric{(prostration)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\subsection{Theotokion and Psalm Verses}

Thou who for our sake wast born of a virgin and didst suffer crucifixion, O good One, and didst despoil death through death and as God didst reveal resurrection: Despise not those whom thou hast created with thine own hand; show forth thy love for mankind, O merciful One; accept the intercession of thy mother, the Theotokos, for us, and save thy despairing people, O our Savior.

Deliver us not up utterly, for thy holy name's sake, neither disannul thou thy covenant, and cause not thy mercy to depart from us, for Abraham's sake, thy beloved, and for Isaac's sake, thy servant, and for Israel's, thy holy one. 

\subsection{Trisagion}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Kontakion}

\rubric{The kontakion of the day can be found starting on page \pageref{weekday} for weekdays. If it is Great Lent, say:}

When the thief beheld the Author of life hanging upon the cross, he said: If thou wert not god, who art here crucified with us, then had the sun not veiled its rays, neither would the earth have shaken with trembling. But do thou, who sufferest for all men, remember me, O Lord, when thou comest in thy kingdom.

Glory to the Father, and to the Son, and to the Holy Spirit.

In the midst, between two thieves, was thy cross found, the balance-beam of righteousness; for while the one was led down to hades by the heaviness of his blaspheming, the other was lightened of his sins, unto the knowledge of things divine, O Christ God, glory to thee.

Both now and ever, and unto ages of ages. Amen.

When she who bare thee beheld upon the cross thee, the Lamb and Shepherd and Savior of the world, she weeping said: The world rejoiceth, in that it hath received redemption, but my inward parts are inflamed as I behold thy crucifixion, which thou sufferest for all men, O my Son and my God.

\rubric{But on Saturday, use \unrubric{Unto thee, O Lord the Author of creation} and on Sunday, use the hypakoe of the proper tone, which can be found starting on page \pageref{resurrectional}.}

\subsection{Prayer of the Hours}

Lord, have mercy. \rubric{(forty times)}

O Christ our God, who at all times and in every hour, in heaven and on earth, art worshiped and glorified; who art longsuffering, merciful and compassionate; who lovest the just and showest mercy upon the sinner; who callest all to salvation through the promise of blessings to come; O Lord, in this hour receive our supplications, and direct our lives according to thy commandments. Sanctify our souls, hallow our bodies, correct our thoughts, cleanse our minds; deliver us from all tribulation, evil and distress. Encompass us with thy holy Angels, that guided and guarded by them, we may attain to the unity of the faith and to the knowledge of thine unapproachable glory, for thou art blessed unto ages of ages. Amen.

Lord have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian and the Trisagion.}

O Lord and Master of my life, take from me the spirit of sloth, meddling, lust of power and idle talk. \rubric{(prostration)}

But give rather the spirit of chastity, humility, patience, and love to thy servant. \rubric{(prostration)}

Yea, O Lord and King, grant me to see my own sins and not to judge my brother, for thou art blessed unto ages of ages. Amen. \rubric{(prostration)}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

\subsection{The Final Prayer}

O Master, Lord Jesus Christ our God, who art longsuffering toward our sins and who hast led us even to the present hour, in which, as thou didst hang upon the life-giving tree thou didst make a way into paradise for the penitent thief and by death didst destroy death: Be gracious unto us sinners and thine unworthy servants; for we have sinned and have dealt iniquitously, and we are not worthy to lift up our eyes and look upon the heights of heaven, inasmuch as we have departed from the path of thy righteousness and have walked after the desires of our own hearts. But we implore of thy boundless goodness: Spare us, O Lord, according to the multitude of thy mercy, and save us, for thy holy name's sake; for our days have passed away in vanity. Wrest us out of the hand of the adversary, and forgive our sins, and mortify our carnal imagination, that, putting off the old man, we may be clothed upon with the new man and may live unto thee, our Master and our Benefactor, and that, so following after thy commandments, we may attain unto rest eternal, where is the abode of all those who rejoice. For thou art, in verity, the true Joy and Exultation of those who love thee, O Christ our God, and unto thee we ascribe glory, together with thine unoriginate Father and thine all-holy and good and life-giving Spirit, now and ever, and unto ages of ages. Amen.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
