\section{Occasional Prayers}

\subsection{Prayers Before Commencing Any Task}

O God, make speed to save me; O Lord, make haste to help me.

Almighty God, our Help and Refuge, Fountain of wisdom and Tower of strength, who knowest that I can do nothing without thy guidance and help; assist me, I pray thee, and direct me to divine wisdom and power, that I may accomplish this task, and whatever I may undertake to do, faithfully and diligently, according to thy will, so that it may be profitable to myself and others, and to the glory of thy Holy Name. For thine is the kingdom, and the power, and the glory, of the Father, and of the Son, and of the Holy Spirit: now and ever, and unto ages of ages. Amen.

O Lord Jesus Christ, Only-begotten Son of the Eternal Father, You have said, “Without Me you can do nothing.” In faith I embrace Your words, O Lord, and bow before Your goodness.Grant me the inclination to be fruitful in labor, and bless my work for Your glory. Amen.

\subsection{Prayers After Completing Any Task}

Blessed art thou, O Lord my God, for thou hast helped me and strengthened me.

Thank You, O Lord, for Your strength and guidance in my work. You are the fulfillment of all good things. Fill also my soul with joy and gladness, that I may praise You, Father, Son, and Holy Spirit, always, now and forever, and to the ages of ages. Amen.

\subsection{A Prayer Before Study}

O Christ my Lord, Giver of light and wisdom, who opened the eyes of the blind man and made the fishermen wise heralds and teachers of the Gospel through the coming of the Holy Spirit, illuminate also my mind with the light of the grace of Your Holy Spirit. Grant me discernment, understanding, and wisdom in learning, that I may abound in every good work and glorify You, together with Your Eternal Father, and Your All-holy, Good, and Life-giving Spirit, always, now and forever, and to the ages of ages. Amen.

\subsection{A Prayer Before Using the Internet}

Be the helper of my soul, O God, for I walk in the midst of many snares. Deliver me from them and save me, for You are good, and You love mankind.

\subsection{A Prayer of a Sick Person}

O Lord Jesus Christ, our Saviour, Physician of souls and bodies, who didst become man and suffer death on the Cross for our salvation, and through thy tender love and compassion didst heal all manner of sickness and affliction; do thou O Lord, visit me in my suffering, and grant me grace and strength to bear this sickness with which I am afflicted, with Christian patience and submission to thy will, trusting in thy loving kindness and tender mercy. Bless, I pray thee, the means used for my recovery, and those who administer them. Let my sickness be for the benefit of my soul, and grant that I may live the rest of my life according to thy will. For thou art the source of life and healing, and to thee I give praise and glory, now and unto ages of ages. Amen.

\subsection{A Prayer for a Sick Person}

O holy Father, heavenly Physician of our souls and bodies, who hast sent thine Only-begotten Son our Lord Jesus Christ to heal all our ailments and deliver us from death: do thou visit and heal thy servant \rubric{(name)}, granting \rubric{him/her} release from pain and restoration to health and vigor, that \rubric{he/she} may give thanks unto thee and bless thy holy Name, of the Father, and of the Son, and of the Holy Spirit: now and ever, and unto ages of ages. Amen. 

\subsection{Thanksgiving After Recovery from Sickness}

Almighty God, our heavenly Father, Source of life and Fountain of all good things, I bless thy Holy Name, and offer to thee most hearty thanks for having delivered me from my sickness and restored me to health. Grant me thy continuing grace, I pray thee, that I may keep my good resolutions and correct the errors of my past life, and improve in virtue, and live a new life in dutiful fear of thee, doing thy will in all things, and devoting this new life which thou has given me to thy service: that thus living for thee, I may be found ready when it pleaseth thee to call me to thee, O heavenly Father, to whom with thine Only-begotten Son, our Lord Jesus Christ, and thine all-holy and Life-giving Spirit, is due all honor, praise, glory, and thanksgiving: now and ever, and unto ages of ages. Amen.

\subsection{Before an Operation}

O Heavenly Father, Creator and Comforter, who created me in Your image and likeness, You know every fiber of my being and have willed me into existence. I implore You, O Lord, to guide the minds and hands of those who will operate on me so that I may be restored to health and well-being. Help me, O Lord, to pray with all my heart, and relieve the burden of concern and anxiety that rests heavily upon me and my family with the knowledge that You are with us, now and always. And when I awake from surgery, take me by Your hand, O Lord, and lead me to a life of peace and thanksgiving. Amen.

\subsection{After an Operation}

O Compassionate Lord, I thank You because You have aided and guided all who assisted in my healing and recovery. Like the woman who touched the hem of Your garment, I too have been freed from the anxiety and isolation of my illness. Bless me, O Lord, with the lovingkindness You so abundantly pour upon me, that I may continuously bear witness to Your healing grace. For blessed and glorified are You forever and ever. Amen.

\subsection{On Moving to a New Home}

O God our Savior, You deigned to enter under the roof of Zacchaeus for his salvation and for the salvation of all in his house. Now, O Lord, keep us who have desired to dwell here safe from all harm, and accept our supplication, unworthy though we are. Bless this habitation, and keep our lives free from all evil. For to You are due all glory, honor, and worship, together with Your Eternal Father, and Your All-holy, Good, and Life-giving Spirit, now and forever, and to the ages of ages. Amen.

\subsection{Prayers for Travel}

O Lord Jesus Christ our God, the true and living way, be thou, O Master, my companion, guide and guardian during my journey; deliver and protect me from all danger, misfortune and temptation; that being so defended by Thy divine power, I may have a peaceful and successful journey and arrive safely at my destination. For in thee I put my trust and hope, and to thee, together with thy Eternal Father, and the All-holy Spirit, I ascribe all praise, honor and glory: now and ever, and unto ages of ages. Amen.

Lord Jesus, You traveled with the two disciples to Emmaus after the resurrection and set their hearts on fire with Your grace. Travel also with me and gladden my heart with Your presence. I know, Lord, that I am a pilgrim on this earth, seeking the citizenship which is in heaven. During my journey surround me with Your holy angels and keep me safe from seen and unseen dangers. Grant that I may carry out my plans and fulfill my expectations according to Your will. Help me to see the beauty of creation and to comprehend the wonder of Your truth in all things. For You are the way, the truth and the life, and to You I give thanks, praise and glory forever. Amen.

\subsection{A Prayer in Time of Need}

Almighty God, Father of mercy and God of all consolation, come to my aid and deliver me from all adversity. For I believe, O Lord, that all trials of this life are under Your care, and that all things work for the good of those who love You. Take away from me fear, anxiety, and distress. Help me to face and endure my difficulties with faith, courage, and wisdom. Grant that this trial may bring me closer to You, for You are my rock and my refuge, my comfort and my hope, my delight and my joy. In Your love and compassion do I place my trust. For blessed is Your name, of the Father, and of the Son, and of the Holy Spirit, now and forevermore. Amen.

\subsection{A Prayer in Temptation}

O Jesus Christ, Sovereign Master, help me and do not let me sin against You. Incline not my heart to words or thoughts of evil, but deliver me from all temptation. Amen.

\subsection{Thanksgiving After Deliverance From Trouble}

Almighty and merciful God, I most humbly and heartily thank thy divine majesty for thy loving kindness and tender mercies, that thou hast heard my humble prayer, and graciously vouchsafed to deliver me from my trouble and misery. Grant me, I beseech thee, thy helping grace, that I may obediently walk in thy holy commandements, and lead a sober, righteous and godly life, ever remembering thy mercies, and the blessings thou hast undeservedly bestowed upon me, that I may continually offer to thee the sacrifice of praise and thanksgiving, O Father, Son, and Holy Spirit.

\subsection{A Prayer for the Dead}

Into thy hands, O Lord, I commend the souls of thy servants, \rubric{(name)}, and beseech thee to grant them rest in the place of thy rest, where all thy blessed Saints repose, and where the light of thy countenance shineth forever. And I beseech thee also to grant that our present lives may be godly, sober, and blameless, that, we too may be made worthy to enter into thy heavenly Kingdom with those we love but see no longer: for thou art the Resurrection, and the Life, and the Repose of thy departed servants, O Christ our God, and unto thee we ascribe glory: to the Father, and to the Son, and to the Holy Spirit; now and ever, and unto ages of ages. Amen.
