\section{Paschal Office}

Through the prayers of our holy fathers, O Lord Jesus Christ our God, have mercy upon us, and save us. Amen.

Christ is risen from the dead, trampling down death by death; and upon those in the tombs bestowing life! \rubric{(thrice)}

In that we have beheld the Resurrection of Christ, let us bow down before the Holy Lord Jesus, the only sinless One. Thy Cross do we adore, O Christ, and Thy Holy Resurrection we praise and glorify: for Thou art our God, and we know none other beside Thee; we call upon Thy Name. O come, all ye faithful, let us adore Christ's Holy Resurrection. For lo, through the Cross is joy come into all the world. Ever blessing the Lord, let us sing His Resurrection: for in that He endured the Cross for us, He hath destroyed Death by death. \rubric{(thrice)}

\rubric{(Tone 4)} They who were with Mary came before the dawn, found the stone rolled away from the sepulcher, and heard the angels say unto them: Why seek ye Him as man with the dead, Who dwells in light eternal? Behold the grave wrappings; make haste and declare to the world that the Lord is risen, and hath caused death to die; for He is the Son of God, the Savior of mankind.

\rubric{(Tone 8)} O Immortal One, when Thou didst descend into the tomb, Thou didst destroy the power of Hades; and Thou didst rise victorious, O Christ God. Thou hast said to the ointment-bearing women: Rejoice! And Thou gavest peace to Thy Disciples, O Bestower of Resurrection to those Who had fallen.

In the grave with the body but in Hades with the soul as God; in paradise with the thief, and on the throne with the Father and the Holy Spirit wast Thou, O Christ, filling all things, Thyself uncircumscribed.

Glory to the Father, and to the Son, and to the Holy Spirit.

As life-bearing, as more splendid than paradise and more radiant than any royal chamber, O Christ, is shown forth from Thy tomb the fountain of our Resurrection.

Both now and ever, and unto ages of ages. Amen.

Rejoice, O thou hallowed, divine abode of the Most High, for through thee, O Theotokos, was joy given unto those who cry aloud to thee: Blessed art thou among women, O all-undefiled Lady.

Lord, have mercy. \rubric{(forty times)}

Glory to the Father, and to the Son, and to the Holy Spirit; both now and ever, and unto ages of ages. Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without corruption bearest God the Word and art truly Theotokos: we magnify thee.

Through the prayers of our holy fathers, O Lord Jesus Christ our God, have mercy upon us, and save us. Amen.

\rubric{When the Paschal Office is said in place of Compline or Evening Prayers, we insert the following prayer of St. Basil the Great:}

Blessed art Thou, O Lord, Master Almighty, Who hast lightened the day with the light of the sun and hast illumined the night with flashes of fire, Who hast vouchsafed us to pass through the length of the day and to draw near to the beginning of the night; hearken to our prayer and to that of all Thy people; and, having pardoned us all our voluntary and involuntary sins, receive our evening supplications, and send down the multitude of Thy mercy and compassions upon Thine inheritance. Wall us in with Thy holy angels. Arm us with the armor of Thy righteousness. Make a bulwark about us with Thy truth. Guard us with Thy power. Deliver us from all oppression and every plot of the adversary. Grant us also that the present evening with the coming night and all the days of our life may be holy, perfect, peaceful and sinless, without stumbling-blocks and without fantasy, through the intercessions of the All-holy Theotokos and of all the saints, who in all ages have been well pleasing unto Thee. For Thine it is to have mercy on us and to save us, O our God, and unto Thee we ascribe glory: to the Father, and to the Son, and to the Holy Spirit; both now and ever, and unto ages of ages. Amen.

Christ is risen from the dead, trampling down death by death; and upon those in the tombs bestowing life! \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit; both now and ever, and unto ages of ages. Amen.

Lord, have mercy. \rubric{(thrice)}

Christ is risen from the dead, trampling down death by death; and upon those in the tombs bestowing life!

\cleardoublepage
