\section{First Hour}

In the Name of the Father, and of the Son, and of the Holy Spirit. Amen.

Glory to thee, our God, glory to thee.

O heavenly King, O Comforter, the Spirit of truth, who art in all places and fillest all things; Treasury of good things and Giver of life: Come and dwell in us and cleanse us from every stain, and save our souls, O gracious Lord.

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever and unto ages of ages. Amen.

O come, let us worship and fall down before God our King. \rubric{(metania)}

O come, let us worship and fall down before Christ our King and our God. \rubric{(metania)}

O come, let us worship and fall down before Christ Himself, our King and our God. \rubric{(metania)}

\subsection{Psalm 5}

Hear my words, O Lord; consider my cry. Attend unto the voice of my supplication, my King, and my God, for unto Thee will I pray, O Lord. Early in the morning shalt Thou hear my voice; early in the morning will I stand before Thee, and Thou shalt watch over me. For Thou art a God that hast no pleasure in wickedness; the evil-doer shall not dwell nigh Thee. Such as be lawless shall not stand in Thy sight, for Thou hatest all them that work iniquity. Thou shalt destroy all them that speak lies; the Lord will abhor the blood-thirsty and deceitful man. But as for me, by the multitude of Thy mercy I will come into Thine house; in Thy fear will I worship toward Thy holy temple. Lead me, O Lord, in Thy righteousness; because of mine enemies, make my way plain before Thee. For there is no truth in their mouth; their heart is vain; their throat is an open sepulcher; they flatter with their tongue. Judge them, O God; let them fall through their own imaginations; cast them out according to the multitude of their ungodliness; for they have embittered Thee, O Lord. And let all them that put their trust in Thee be glad; they shall ever rejoice; and Thou shalt dwell in them and they that love Thy Name shall be joyful in Thee. For Thou wilt bless the righteous, O Lord, for with the shield of Thy favorable kindness hast Thou crowned us.

\subsection{Psalm 89}

Lord, Thou hast been our refuge from generation to generation. Before ever the mountains were formed, or the earth and the world were created, even from age to age Thou art. Turn not man away unto humiliation; yea, Thou hast said, Be converted, ye children of men. For a thousand years before Thine eyes, O Lord, are but as yesterday when it is past, and as a watch in the night. Fleeting shall their years be; he shall go by in the morning like the grass; in the morning it shall flourish, and grow up, but in the evening it shall fall away, and dry up, and wither. For we consumed away in Thy displeasure, and were troubled at Thy wrathful indignation. Thou hast set our misdeeds before Thee, our years are in the light of Thy countenance. For all our days are spent, and we have disappeared in Thy wrath; Our years are spun out like a spider’s web. The days of our age are threescore years and ten, or if we be so strong, fourscore years, and more than these is but labor and sorrow; for frailty shall come upon us, and we shall be chastened. Who knoweth the power of Thy wrath, and from fear of Thee, who can recount Thine anger? So make Thy right hand known to me, and to them that are bound by the heart in wisdom. Turn Thee again, O Lord; how long? And be gracious unto Thy servants. We were satisfied with Thy mercy in the morning, O Lord, and we rejoiced and were glad; We were glad all our days; for the days wherein Thou didst humble us, the years wherein we saw adversity. And look upon Thy servants, and upon Thy works, and guide their children, and let the brightness of the Lord our God be upon us, and prosper Thou the work of our hands upon us; yea, prosper Thou our handy-work.

\subsection{Psalm 100}

Mercy and judgment shall be my song unto Thee, O Lord; I sing and understand in a blameless way; when wilt Thou come unto me? I have walked in the innocency of my heart in the midst of my house. I have set no unlawful thing before mine eyes; I have hated the workers of iniquity. A froward heart hath not cleaved unto me; I did not know the crafty man that turned away from me. Whoso privily slandereth his neighbor, him did I drive out; whoso hath a proud look and a greedy stomach, with such I did not eat. Mine eyes look upon such as are faithful in the land, that they may dwell with me; whoso leadeth a godly life, he shall be my servant. The proud doer hath not dwelt in the midst of my house; he that speaketh unjustly shall have no place in my sight. In the morning I slew all the sinners of the land, to consume all the workers of lawlessness from the city of the Lord.

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Alleluia, alleluia, alleluia. Glory to thee, O God. \rubric{(thrice)}

Lord, have mercy. \rubric{(thrice)}

\subsection{Troparia and Verses}

\rubric{If it is a weekday of Great Lent, the following troparia and verses are sung in Tone 6, else we say \unrubric{Glory...}, the troparion of the day, then \unrubric{Both now...}. The troparion of the day can be found starting on page \pageref{weekday}.}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

In the morning attend unto the voice of my supplication, O my King and my God. \rubric{(prostration)}

\rubric{Verse 1:} Unto my words give ear, O Lord; hear my cry. \rubric{(prostration)}

\rubric{Verse 2:} For unto thee will I pray, O Lord: thou shalt hearken in the morning to my voice. \rubric{(prostration)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\subsection{Theotokion and Psalm Verses}

What shall I call thee, O thou who art full of grace? Heaven, for from thee shone forth the Sun of righteousness; Paradise, for thou hast budded forth the Flower of immortality; Virgin, for thou hast remained incorrupt; Pure Mother, for thou hast held in thy holy embrace a Son, who is God of all. Beseech thou him to save our souls.

My steps do thou direct according to thy saying, and so let no iniquity have dominion over me. \rubric{(twice in Lent)}

Deliver me from the false accusation of men, and I will keep thy commandments. \rubric{(twice in Lent)}

Make thy face to shine upon thy servant, and teach me thy statutes. \rubric{(twice in Lent)}

Let my mouth be filled with thy praise, O Lord, that I may hymn thy glory and thy majesty all the day long. \rubric{(thrice in Lent)}

\subsection{Trisagion}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Kontakion}

\rubric{The kontakion of the day can be found starting on page \pageref{weekday}. If it is Great Lent, use the following kontakia:}

\rubric{Monday, Tuesday, Thursday:} With hearts and mouths let us continually magnify the glorious Mother of God, more holy than the angels, confessing her to be the Theotokos, who did, in very truth, bring forth God incarnate and who unceasingly doth intercede for our souls.

\rubric{Wednesday, Friday:} Quickly go before us, O Christ our God, lest the enemy which blasphemeth thee and constraineth us, lead us into captivity. Overcome by the cross those who war against us, that they may know what power hath the faith of Orthodox believers; through the intercessions of the Theotokos, O thou who alone lovest mankind.

\rubric{Saturday:} Unto thee, O Lord, the Author of creation, the universe doth offer the God-bearing martyrs as the first-fruits of nature. By whose prayers, through the Theotokos, do thou preserve thy Church in profound peace, O most merciful One.

\rubric{On Sunday, use the hypakoe of the proper tone, which can be found starting on page \pageref{resurrectional}.}

\subsection{Prayer of the Hours}

Lord, have mercy. \rubric{(forty times)}

O Christ our God, who at all times and in every hour, in heaven and on earth, art worshiped and glorified; who art longsuffering, merciful and compassionate; who lovest the just and showest mercy upon the sinner; who callest all to salvation through the promise of blessings to come; O Lord, in this hour receive our supplications, and direct our lives according to thy commandments. Sanctify our souls, hallow our bodies, correct our thoughts, cleanse our minds; deliver us from all tribulation, evil and distress. Encompass us with thy holy Angels, that guided and guarded by them, we may attain to the unity of the faith and to the knowledge of thine unapproachable glory, for thou art blessed unto ages of ages. Amen.

Lord have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian and the Trisagion.}

O Lord and Master of my life, take from me the spirit of sloth, meddling, lust of power and idle talk. \rubric{(prostration)}

But give rather the spirit of chastity, humility, patience, and love to thy servant. \rubric{(prostration)}

Yea, O Lord and King, grant me to see my own sins and not to judge my brother, for thou art blessed unto ages of ages. Amen. \rubric{(prostration)}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

\subsection{The Final Prayer}

O Christ, the true Light, which illumineth and sanctifieth every man who cometh into the world: Let the light of thy countenance be signed upon us, that in it we may behold the light unapproachable. Guide our footsteps aright, to the keeping of thy commandments, through the intercessions of thine all-immaculate Mother and of all thy saints. Amen.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
