\section{Third Hour}

In the Name of the Father, and of the Son, and of the Holy Spirit. Amen.

Glory to thee, our God, glory to thee.

O heavenly King, O Comforter, the Spirit of truth, who art in all places and fillest all things; Treasury of good things and Giver of life: Come and dwell in us and cleanse us from every stain, and save our souls, O gracious Lord.

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever and unto ages of ages. Amen.

O come, let us worship and fall down before God our King. \rubric{(metania)}

O come, let us worship and fall down before Christ our King and our God. \rubric{(metania)}

O come, let us worship and fall down before Christ Himself, our King and our God. \rubric{(metania)}

\subsection{Psalm 16}

Hear my just cause, O Lord; attend unto my supplication. Hearken unto my prayer, that goeth not out of flattering lips. From Thy presence shall my judgment come forth; let mine eyes look upon the things that are right. Thou hast proved my heart; Thou hast visited in the night. Thou hast tried me, and unrighteousness hath not been found within me. That my mouth shall not speak of men’s works, for the sake of the words of Thy lips I have kept hard ways. O hold Thou up my goings in Thy paths, that my footsteps slip not. I called, for Thou hast heard me, O God; incline Thine ear to me, and hearken unto my words. Make Thy mercies marvelous, Thou that art the Savior of them which put their trust in Thee, from such as resist Thy right hand. Keep me, O Lord, as the apple of Thine eye; hide me under the shelter of Thy wings, from the presence of the ungodly that trouble me; mine enemies compass my soul round about. They are enclosed in their own fat, and their mouth speaketh proud things. They that cast me out have now surrounded me; they have turned their eyes down to the ground, like as a lion that is greedy of his prey, and as it were a lion’s whelp, lurking in secret places. Arise, O Lord, disappoint them, and trip them up; deliver my soul from the ungodly, Thy sword from the enemies of Thy hand. O Lord, divide them in their life from the few of the earth; yea, from Thy hid treasure hath their belly been filled. They had children at their desire, and left the rest of their substance for their babes. But as for me, in righteousness shall I appear before Thy face; when Thy glory is revealed, I shall be satisfied.

\subsection{Psalm 24}

Unto thee, O Lord, have I lifted up my soul; my God, I have put my trust in Thee: O let me never be confounded, neither let mine enemies laugh me to scorn; for all they that wait on Thee shall not be ashamed. Let them be ashamed such as transgress without a cause. Tell me Thy ways, O Lord, and teach me Thy paths. Lead me forth unto Thy truth, and teach me, for Thou art God my Savior, and upon Thee have I waited all the day long; remember Thy loving-kindnesses, O Lord, and Thy mercies, which are from everlasting. O remember not the sins of my youth, and of mine ignorance; according to Thy mercy think Thou upon me, O Lord, for Thy goodness’ sake. Gracious and righteous is the Lord, therefore will He give a Law to sinners in the way. He will guide the meek unto judgment, He shall teach the meek His ways. All the paths of the Lord are mercy and truth unto such as keep His covenant, and His testimonies. For Thy Name’s sake, O Lord, be merciful unto my sin, for it is great. What man is he, that feareth the Lord? To him shall He give a Law in the way which He hath chosen. His soul shall dwell at ease, and his seed shall inherit the land. The Lord is the strength of them that fear Him, and He will show them His covenant. Mine eyes are ever toward the Lord, for He shall pluck my feet out of the net. Be charitable unto me, and have mercy on me, for I am only-begotten and poor. The sorrows of my heart are enlarged; O bring Thou me out of my troubles. Look upon my humbleness and my hardship, and forgive all my sins. Consider mine enemies, how many they are, and they bear a tyrannous hate against me. O keep my soul, and deliver me; let me not be confounded, for I have put my trust in Thee. The innocent and the upright have cleaved unto me, for I waited upon Thee, O Lord. Deliver Israel, O God, out of all his troubles.

\subsection{Psalm 50}

Have mercy upon me, O God, according to thy great mercy: according to the multitude of thy tender mercies blot out mine iniquity. Wash me thoroughly from mine iniquity, and cleanse me from my sin. For I acknowledge mine iniquity, and my sin is ever before me. Against thee only have I sinned, and done evil in thy sight: that thou mightest be justified in thy words, and prevail when thou art judged. For behold, I was shapened in iniquity, and in sins did my mother conceive me.  For behold, thou hast loved truth: the unclear and hidden things of thy wisdom thou hast made clear to me. Thou shalt sprinkle me with hyssop, and I shall be clean; thou shalt wash me, and I shall be whiter than snow. Thou shalt make me to hear joy and gladness; the bones which thou hast broken shall rejoice. Turn away thy face from my sins, and blot out all mine iniquities. Create in me a clean heart, O God, and renew a right spirit within me. Cast me not away from thy presence, and take not thy Holy Spirit from me. Restore unto me the joy of thy salvation, and steady me with a guiding spirit.  Then will I teach transgressors thy ways, and the impious shall be converted unto thee. Deliver me from bloodguiltiness, O God, thou God of my salvation, and my tongue shall sing aloud of thy righteousness. O Lord, open thou my lips, and my mouth shall declare thy praise. For hadst thou desired sacrifice, I would have given it thee; thou delightest not in burnt offerings. Sacrifices to God are a contrite spirit: a contrite and humble heart, O God, thou wilt not despise. Do good, O Lord, in thy good will unto Zion, that the walls of Jerusalem may be built up. Then shalt thou be pleased with the sacrifice of righteousness, with burnt offering and whole burnt offerings; Then shall they offer bullocks upon thine altar.

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Alleluia, alleluia, alleluia. Glory to thee, O God. \rubric{(thrice)}

Lord, have mercy. \rubric{(thrice)}

\subsection{Troparia and Verses}

\rubric{If it is a weekday of Great Lent, the following troparia and verses are sung in Tone 6, else we say \unrubric{Glory...}, the troparion of the day, then \unrubric{Both now...}. The troparion of the day can be found starting on page \pageref{weekday}.}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\rubric{If it is a weekday of Great Lent, the following troparia and verses are sung in Tone 6, else we say \unrubric{Glory...}, the troparion of the day, then \unrubric{Both now...}}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

O Lord, who at the third hour didst send down upon thine apostles thy Holy Spirit: Take not the same from us, O good One, but renew him in us who pray unto thee. \rubric{(prostration)}

\rubric{Verse 1:} Create in me a clean heart, O God, and renew a right spirit within me. \rubric{(prostration)}

\rubric{Verse 2:} Cast me not away from thy presence, and take not thy Holy Spirit from me. \rubric{(prostration)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\subsection{Theotokion and Psalm Verses}

O Theotokos, thou art the true vine who didst bud forth for us the Fruit of life. Implore thou him, we beseech thee, O Lady, together with the apostles and all the saints, that he will have mercy on our souls.

Blessed is the Lord God, blessed is the Lord day by day; the God of our salvation shall prosper us along the way. Our God is the God of salvation.

\subsection{Trisagion}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Kontakion}

\rubric{The kontakion of the day can be found starting on page \pageref{weekday}. If it is Great Lent, say:}

Blessed art thou, O Christ our God, who hast revealed the fishermen as all-wise by sending down upon them the Holy Spirit; through them thou didst draw the world into thy net. O Lover of mankind, glory to thee.

Glory to the Father, and to the Son, and to the Holy Spirit.

Grant speedy and steadfast consolation unto thy servants, O Jesus, when our spirits are cast down within us. Depart not from our souls in affliction. Be not far from our thoughts in time of trouble, but always defend us. Draw near unto us, draw near unto us, thou who art everywhere present. As thou art ever with thine apostles, so, also, O compassionate One, unite thyself unto those who long for thee, that with one accord we may sing praises unto thee and glorify thine all-holy Spirit.

Both now and ever, and unto ages of ages. Amen.

The hope and protection and refuge of Christians art thou, the impregnable wall and the haven unvexed by storms, O immaculate Theotokos; but in that thou dost save the world by thine unceasing intercessions, call thou us also to remembrance, O all-lauded Virgin.

\rubric{But on Saturday, use \unrubric{Unto thee, O Lord the Author of creation} and on Sunday, use the hypakoe of the proper tone, which can be found starting on page \pageref{resurrectional}.}

\subsection{Prayer of the Hours}

Lord, have mercy. \rubric{(forty times)}

O Christ our God, who at all times and in every hour, in heaven and on earth, art worshiped and glorified; who art longsuffering, merciful and compassionate; who lovest the just and showest mercy upon the sinner; who callest all to salvation through the promise of blessings to come; O Lord, in this hour receive our supplications, and direct our lives according to thy commandments. Sanctify our souls, hallow our bodies, correct our thoughts, cleanse our minds; deliver us from all tribulation, evil and distress. Encompass us with thy holy Angels, that guided and guarded by them, we may attain to the unity of the faith and to the knowledge of thine unapproachable glory, for thou art blessed unto ages of ages. Amen.

Lord have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian and the Trisagion.}

O Lord and Master of my life, take from me the spirit of sloth, meddling, lust of power and idle talk. \rubric{(prostration)}

But give rather the spirit of chastity, humility, patience, and love to thy servant. \rubric{(prostration)}

Yea, O Lord and King, grant me to see my own sins and not to judge my brother, for thou art blessed unto ages of ages. Amen. \rubric{(prostration)}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

\subsection{The Final Prayer}

O Master God, Almighty Father, O Lord, the only-begotten Son Jesus Christ, and O Holy Spirit, one Godhead and one Power: Have mercy on me a sinner; and by the judgments which thou hast established, save me, thine unworthy servant, for thou art blessed unto ages of ages. Amen.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
