\section{Typika}

In the Name of the Father, and of the Son, and of the Holy Spirit. Amen.

Glory to thee, our God, glory to thee.

O heavenly King, O Comforter, the Spirit of truth, who art in all places and fillest all things; Treasury of good things and Giver of life: Come and dwell in us and cleanse us from every stain, and save our souls, O gracious Lord.

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever and unto ages of ages. Amen.

\subsection{Psalm 102}

\rubric{(Tone 8)} Bless the Lord, O my soul: and all that is within me, bless his holy name. Bless the Lord, O my soul, and forget not all his benefits: who forgiveth all thine iniquities; who healeth all thy diseases; who redeemeth thy life from destruction; who crowneth thee with lovingkindness and tender mercies; who satisfieth thy mouth with good things; so that thy youth is renewed like the eagle's. The Lord executeth righteousness and judgment for all that are oppressed. He made known his ways unto Moses, his acts unto the children of Israel. The Lord is merciful and gracious, slow to anger, and plenteous in mercy. He will not always chide: neither will he keep his anger forever. He hath not dealt with us after our sins; nor rewarded us according to our iniquities. For as the heaven is high above the earth, so great is his mercy toward them that fear him. As far as the east is from the west, so far hath he removed our transgressions from us. Like as a father pitieth his children, so the Lord pitieth them that fear him. For he knoweth our frame; he remembereth that we are dust. As for man, his days are as grass: as a flower of the field, so he flourisheth. For the wind passeth over it, and it is gone; and the place thereof shall know it no more. But the mercy of the Lord is from everlasting to everlasting upon them that fear him, and his righteousness unto children's children; to such as keep his covenant, and to those that remember his commandments to do them. The Lord hath prepared his throne in the heavens; and his kingdom ruleth over all. Bless the Lord, ye his angels, that excel in strength, that do his commandments, hearkening unto the voice of his word. Bless ye the Lord, all ye his hosts; ye ministers of his, that do his pleasure. Bless the Lord, all his works in all places of his dominion: bless the Lord, O my soul.

\subsection{Psalm 145}

\rubric{(Tone 2)} Glory to the Father, and to the Son, and to the Holy Spirit.

Praise the Lord, O my soul; While I live will I praise the Lord; I will sing unto my God as long as I have being. O put not your trust in princes, in the sons of men, in whom there is no salvation. His spirit shall go forth, and he shall return again to his earth; in that day all his thoughts shall perish. Blessed is he that hath the God of Jacob for his helper, whose hope is in the Lord his God; Who made heaven and earth, the sea, and all that therein is, Who preserveth truth for ever; Who rendereth judgment for the wronged, Who giveth food unto the hungry; the Lord looseth the fettered; The Lord giveth wisdom to the blind; the Lord raiseth up the fallen; the Lord loveth the righteous; The Lord preserveth the proselytes; He defendeth the fatherless and the widow, but the way of sinners shall He destroy. The Lord shall reign for ever, Thy God, O Zion, unto generation and generation.

\subsection{O Only-Begotten}

Both now and ever and unto ages of ages. Amen.

O only-begotten Son and immortal Word of God, who for our salvation didst will to be incarnate, of the holy Theotokos and ever-virgin Mary and without change didst become man and wast crucified, O Christ our God, trampling down Death by death, who art one of the Holy Trinity, glorified with the Father and the Holy Spirit: Save us.

\subsection{The Beatitudes in Tone Eight}

In thy kingdom remember us, O Lord, when thou comest in thy kingdom.

Blessed are the poor in spirit, for theirs is the kingdom of heaven.

Blessed are those who mourn, for they shall be comforted.

Blessed are the meek, for they shall inherit the earth.

Blessed are those who hunger and thirst for righteousness, for they shall be satisfied.

Blessed are the merciful, for they shall obtain mercy.

Blessed are the pure in heart, for they shall see God.

Blessed are the peacemakers, for they shall be called the sons of God.

Blessed are those who are persecuted for righteousness' sake, for theirs is the kingdom of heaven.

Blessed are you when men revile you and persecute you and utter all kinds of evil against you falsely on my account.

Rejoice and be glad, for your reward is great in heaven.

Glory to the Father, and to the Son, and to the Holy Spirit.

Both now and ever, and unto ages of ages. Amen.

\subsection{The Readings}

\rubric{The appointed epistle and gospel readings are now read, not intoned, from a Bible. Each reading is simply introduced and read, the usual congregational responses being omitted.}

\subsection{Troparia and Verses}

The heavenly choir singeth thy praises, saying: Holy, holy, holy, Lord of Sabaoth; heaven and earth are full of thy glory.

Come unto him, and be enlightened, and your faces shall not be ashamed.

The heavenly choir singeth thy praises, saying: Holy, holy, holy, Lord of Sabaoth; heaven and earth are full of thy glory.

Glory to the Father, and to the Son, and to the Holy Spirit.

The choir of the holy angels and archangels, with all the powers of heaven, singeth thy praises, saying: Holy, holy, holy, Lord of Sabaoth; heaven and earth are full of thy glory.

Both now and ever, and unto ages of ages. Amen.

\subsection{The Creed}

I believe in one God, the Father Almighty, Maker of heaven and earth, and of all things visible and invisible;

And in one Lord Jesus Christ, the Son of God, the Only-begotten, Begotten of the Father before all worlds, Light of Light, Very God of Very God, Begotten, not made; of one essence with the Father, by whom all things were made:

Who for us men and for our salvation came down from heaven, and was incarnate of the Holy Spirit and the Virgin Mary, and was made man;

And was crucified also for us under Pontius Pilate, and suffered and was buried;

And the third day He rose again, according to the Scriptures;

And ascended into heaven, and sitteth at the right hand of the Father;

And He shall come again with glory to judge the quick and the dead, Whose kingdom shall have no end.

And I believe in the Holy Spirit, the Lord, and Giver of Life, Who proceedeth from the Father, Who with the Father and the Son together is worshiped and glorified, Who spake by the Prophets;

And I believe in One Holy Catholic and Apostolic Church.

I acknowledge one Baptism for the remission of sins.

I look for the Resurrection of the dead.

And the Life of the world to come. Amen.

Forgive, remit, pardon, O God, our sins, both voluntary and involuntary, in deed and in word, in knowledge or in ignorance, committed by night or by day, in mind and in thought. Forgive us them all, for thou art good and lovest mankind.

Our Father, who art in heaven, hallowed be thy Name; thy kingdom come; thy will be done on earth, as it is in heaven. Give us this day our daily bread; and forgive us our trespasses, as we forgive those who trespass against us; and lead us not into temptation, but deliver us from evil.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Prayer of the Hours}

Lord, have mercy. \rubric{(forty times)}

O Christ our God, who at all times and in every hour, in heaven and on earth, art worshiped and glorified; who art longsuffering, merciful and compassionate; who lovest the just and showest mercy upon the sinner; who callest all to salvation through the promise of blessings to come; O Lord, in this hour receive our supplications, and direct our lives according to thy commandments. Sanctify our souls, hallow our bodies, correct our thoughts, cleanse our minds; deliver us from all tribulation, evil and distress. Encompass us with thy holy Angels, that guided and guarded by them, we may attain to the unity of the faith and to the knowledge of thine unapproachable glory, for thou art blessed unto ages of ages. Amen.

Lord have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Blessed be the name of the Lord, henceforth and forevermore. \rubric{(thrice with metanias)}

\subsection{Psalm 33}

I will bless the Lord at all times, His praise is ever in my mouth. In the Lord shall my soul be praised; let the meek hear, and be glad. O magnify the Lord with me, and we shall exalt His Name together. I sought the Lord and He heard me, yea, He delivered me out of all my troubles. Come unto Him, and be enlightened, and your faces shall not be ashamed. This poor man cried and the Lord heard him, and saved him out of all his troubles. The angel of the Lord tarrieth round about them that fear Him, and delivereth them. O taste, and see, that the Lord is good; blessed is the man that trusteth in Him. O fear the Lord, all ye that are His saints, for they that fear Him lack nothing. The rich have lacked, and suffered hunger, but they that seek the Lord shall want no manner of thing that is good. Come, ye children, and hearken unto me; I will teach you the fear of the Lord. What man is he that lusteth to live, and would gladly see good days? Keep thy tongue from evil, and thy lips, that they speak no guile. Shun evil, and do good; seek peace, and pursue it. The eyes of the Lord are over the righteous, and His ears are open unto their prayers. But the countenance of the Lord is against them that do evil, to root out the remembrance of them from the earth. The righteous cried, and the Lord heard them, and delivered them out of all their troubles. The Lord is nigh unto them that are of a contrite heart, and will save such as be of an humble spirit. Many are the troubles of the righteous, but the Lord delivereth them out of all. The Lord keepeth all their bones; not one of them shall be broken. The death of sinners is evil, and they that hate the righteous shall sin greatly. The Lord will deliver the souls of His servants, and all they that put their trust in Him shall do no sin.

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

It is truly meet to bless thee, O Theotokos, ever blessed and all-blameless, and the mother of our God. More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

\subsection{Synaxarion}

\rubric{The appropriate synaxarion readings for the day may optionally be read now, followed by a brief spiritual message if someone has been blessed to give one, or an appropriate reading from a Church Father or other Orthodox text. Any necessary announcements should be made, then the service concludes with:}

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
