\section{Selections from Vespers}

\subsection{Psalm 103}

Bless the Lord, O my soul. O Lord my God, thou art very great; thou art clothed with honor and majesty. Who coverest thyself with light as with a garment: who stretchest out the heavens like a curtain: Who layeth the beams of his chambers in the waters: who maketh the clouds his chariot: who walketh upon the wings of the wind: Who maketh his angels spirits; his ministers a flaming fire: Who laid the foundations of the earth, that it should not be removed forever. Thou coveredst it with the deep as with a garment: the waters stood above the mountains. At thy rebuke they fled; at the voice of thy thunder they hasted away. They go up by the mountains; they go down by the valleys unto the place which thou hast founded for them. Thou has set a bound that they may not pass over; that they turn not again to cover the earth. He sendeth the springs into the valleys, which run among the hills. They give drink to every beast of the field; the wild asses quench their thirst. By them shall the fowls of the heaven have their habitation, which sing among the branches. He watereth the hills from his chambers: the earth is satisfied with the fruit of thy works. He causeth the grass to grow for the cattle, and herb for the service of man: that he may bring forth food out of the earth: And wine that maketh glad the heart of man, and oil to make his face to shine, and bread which strengtheneth man's heart. The trees of the Lord are full of sap; the cedars of Lebanon, which he hath planted; Where the birds make their nests: as for the stork, the fir trees are her house. The high hills are a refuge for the wild goats; and the rocks for the conies. He appointed the moon for seasons: the sun knoweth his going down. Thou makest darkness, and it is night: wherein all the beasts of the forest do creep forth. The young lions roar after their prey, and seek their meat from God. The sun ariseth, they gather themselves together, and lay them down in their dens. Man goeth forth unto his work and to his labor until the evening. O Lord, how manifold are thy works! in wisdom hast thou made them all: the earth is full of thy riches. So is this great and wide sea, wherein are things creeping, innumerable, both small and great beasts. There go the ships: there is that Leviathan, whom thou hast made therein. These wait all upon thee; that thou mayest give them their meat in due season. That thou givest them they gather: thou openest thine hand, they are filled with good. Thou hidest thy face, they are troubled: thou takest away their breath, they die, and return to their dust. Thou sendest forth thy spirit, they are created: and thou renewest the face of the earth. The glory of the Lord shall endure forever: the Lord shall rejoice in his works. He looketh on the earth, and it trembleth: he toucheth the hills, and they smoke. I will sing unto the Lord as long as I live: I will sing praise to my God while I have my being. My meditation of him shall be sweet: I will be glad in the Lord. Let the sinners be consumed out of the earth, and let the wicked be no more. Bless thou the Lord, O my soul. Praise ye the Lord.

\subsection{Prayers at the Lighting of the Lamps}
\rubric{(1.)} O Lord, compassionate and merciful, long-suffering and plenteous in mercy, give ear to our prayer, and attend to the voice of our supplication. Work upon us a sign for good. Lead us in thy way, that we may walk in thy truth. Make glad our hearts, that we may fear thy holy name. For thou art great and doest wonders. Thou alone art God, and among all the gods there is none like unto thee, O Lord, mighty in mercy, gracious in strength, to aid and to comfort and to save all those who put their trust in thy holy name. For unto thee are due all glory, honor and worship to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(2.)} O Lord, rebuke us not in thy displeasure, neither chasten us in thy wrath, but deal with us according to thy mercy, O Physician and Healer of our souls. Guide us unto the haven of thy will. Enlighten the eyes of our hearts to the knowledge of thy truth, and vouchsafe that the remainder of this day and our whole life may be peaceful and without sin, through the intercessions of the holy Theotokos and of all the saints. For thine is the might, and thine is the kingdom and the power and the glory of the Father and of the Son and of the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(3.)} O Lord our God, remember us sinners and thine unprofitable servants when we call upon thy holy name, and put us not to shame in our expectation of thy mercy; but grant us, O Lord, all our petitions which are unto salvation, and vouchsafe that we may love and fear thee with all our hearts and do thy will in all things. For thou art a good God and lovest mankind, and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(4.)} O thou who, with never-silent hymns and never-ceasing songs of praise to thy glory, art hymned by the holy powers: Fill our mouths with thy praise, that we may magnify thy holy name. And grant unto us part and inheritance with all those who fear thee in truth and keep thy commandments, through the intercessions of the holy Theotokos and of all thy saints. For unto thee are due all glory, honor and worship to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(5.)} O Lord, O Lord, who upholdest all things in the undefiled hollow of thy hand, who showest long-suffering upon us all and repentest thee at our wickedness: Remember thy compassions and thy mercy. Visit us with goodness, and grant that, through the remainder of the present day, by thy grace, we may avoid the diverse subtle snares of the evil one and preserve our lives unassailed, through the grace of thine allhly Spirit. Through the mercy and love toward mankind of thine only-begotton Son, with whom thou art blessed, together with thine all-holy and good and life-giving Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(6.)} O God, great and wonderful, who with wisdom inscrutable and great riches of providence orderest all things and bestowest upon us earthly good things, who hast given us a pledge of the promised kingdom through the good things already bestowed upon us and hast made us to shun all evil during that part of the day which is past: Grant that we may also fulfill the remainder of this day without reproach before thy holy glory and hymn thee, the only good One, our God, who lovest mankind. For thou art our God and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(7.)} O great and most high God, who alone hast immortality and dwellest in light unapproachable, who hast made all creation in wisdom, who hast divided the light from the darkness and hast appointed the sun to rule the day, the moon and stars also to rule the night, who hast vouchsafed unto us sinners at this present hour also to come before thy presence with confession and to offer unto thee our evening praise: Do thou thyself, O Lord who lovest mankind, direct our prayer as incense before thee, and accept it as a savour of sweet-smelling fragrance, and grant that we may pass the present evening and the com ing night in peace. Endue us with the armour of light. Deliver us from the terror of the night and from everything that walketh in darkness, and grant that the sleep which thou hast appointed for the repose of our weakness may be free from every imagination of the devil. Yea, O Master of all, Bestower of good things, may we, being moved to compunction upon our beds, call to remembrance thy name in the night, that, enlightened by meditation on thy commandments, we may rise up in joyfulness of soul to glorify thy goodness, offering up unto thy tender love prayers and supplications for our sins and for those of all thy people, whom do thou visit in mercy, through the intercessions of the holy Theotokos. For thou art a good God and lovest mankind, and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\subsection{Psalm 140}
%\enlargethispage{-\baselineskip} % Widow prevention
O Lord, I have cried out unto thee, hear me: give ear to the voice of my supplication, when I cry out unto thee. Let my prayer be set forth before thee as incense; and the lifting up of my hands as the evening sacrifice.  Set a watch, O Lord, before my mouth and a protecting door about my lips. Incline not my heart to evil words, to make excuses in sins with men that work iniquities, and I will not communicate with the choicest of them. The just man shall correct me in mercy and shall reprove me, but let not the oil of the sinner anoint my head, for my prayer also shall still be against the things with which they are well pleased. Their judges falling upon the rock have been swallowed up. They shall hear my words for they are sweet. As when the thickness of the earth is broken up upon the ground, their bones are scattered by the side of hell. But to thee, O Lord, Lord, are mine eyes. In thee have I put my trust. Take not away my soul. Keep me from the snare which they have laid for me, and the traps of the workers of iniquity. Let the wicked fall into their own nets, while I alone escape.

\subsection{Psalm 141}

I cried unto the Lord with my voice, with my voice unto the Lord did I make my supplication. I poured out my supplication before him, I showed before him my trouble. When my spirit was overwhelmed within me, then thou didst know my path. In the way wherein I walked, have they secretly laid a snare for me. I looked on my right hand and beheld, but there was no one that would know me. Refuge failed me, no one cared for my soul. I cried unto thee, O Lord. I said, Thou art my refuge and my portion in the land of the living. Attend unto my cry, for I am brought very low. Deliver me from my persecutors, for they are stronger than I. Bring my soul out of prison, that I may praise thy name. For the righteous shall wait for me, until thou recompense me.

\subsection{Psalm 129}

Out of the depths have I cried unto thee, O Lord, Lord hear my voice. Let thine ears be attentive to the voice of my supplication.  If thou, O Lord, shouldest mark iniquities, O Lord, who shall stand? For with thee there is forgiveness. Because of thy name have I waited for thee, O Lord. My soul hath waited upon thy word. My soul hath hoped in the Lord. From the morning watch until night, from the morning watch, let Israel trust in the Lord. For with the Lord there is mercy, and with him is abundant redemption, and he shall deliver Israel from all his iniquities.

\subsection{Psalm 116}

Praise the Lord, all ye nations. Praise him all ye people. For his mercy is great toward  us, and the truth of the Lord endureth forever.

\subsection{Phos hilaron}

O Gladsome Light of the holy glory, of the immortal, heavenly, holy, blessed Father, O Jesus Christ: we that come to the setting of the sun, when we behold the evening light, praise Father, Son, and Holy Spirit, God. Meet it is for Thee at all times to be praise with gladsome voices, O Son of God, giver of life; wherefore the whole world doth glorify Thee.

\subsection{Evening Prayer}

Vouchsafe, O Lord, to keep us this night without sin. Blessed art thou, O Lord, the God of our fathers, and praise and glorified is thy Name forever. Amen.

Let thy mercy be upon us, O Lord, even as we have set our hope on thee. Blessed art thou, O Lord; teach me thy statutes. Blessed art thou, O Master; make me to understand thy commandments. Blessed art thou, O Holy One; enlighten me with thy precepts.

Thy mercy, O Lord, endureth forever: O despise not the works of thy hands. To thee belongeth worship, to thee belongeth praise, to thee belongeth glory: to the Father, and to the Son, and to the Holy Spirit: now and ever, and unto ages of ages. Amen.

\subsection{St. Simeon's Prayer}

Lord, now lettest thou thy servant depart in peace, according to thy word: for mine eyes have seen thy salvation, which thou hast prepared before the face of all people; a light to lighten the Gentiles, and the glory of thy people Israel.

\cleardoublepage
