% source: A Psalter for Prayer
Hear my just cause, O Lord; attend unto my supplication. Hearken unto my prayer, that goeth not out of flattering lips. From Thy presence shall my judgment come forth; let mine eyes look upon the things that are right. Thou hast proved my heart; Thou hast visited in the night. Thou hast tried me, and unrighteousness hath not been found within me. That my mouth shall not speak of men’s works, for the sake of the words of Thy lips I have kept hard ways. O hold Thou up my goings in Thy paths, that my footsteps slip not. I called, for Thou hast heard me, O God; incline Thine ear to me, and hearken unto my words. Make Thy mercies marvelous, Thou that art the Savior of them which put their trust in Thee, from such as resist Thy right hand. Keep me, O Lord, as the apple of Thine eye; hide me under the shelter of Thy wings, from the presence of the ungodly that trouble me; mine enemies compass my soul round about. They are enclosed in their own fat, and their mouth speaketh proud things. They that cast me out have now surrounded me; they have turned their eyes down to the ground, like as a lion that is greedy of his prey, and as it were a lion’s whelp, lurking in secret places. Arise, O Lord, disappoint them, and trip them up; deliver my soul from the ungodly, Thy sword from the enemies of Thy hand. O Lord, divide them in their life from the few of the earth; yea, from Thy hid treasure hath their belly been filled. They had children at their desire, and left the rest of their substance for their babes. But as for me, in righteousness shall I appear before Thy face; when Thy glory is revealed, I shall be satisfied.
