% source: A Psalter for Prayer
Unto thee, O Lord, have I lifted up my soul; my God, I have put my trust in Thee: O let me never be confounded, neither let mine enemies laugh me to scorn; for all they that wait on Thee shall not be ashamed. Let them be ashamed such as transgress without a cause. Tell me Thy ways, O Lord, and teach me Thy paths. Lead me forth unto Thy truth, and teach me, for Thou art God my Savior, and upon Thee have I waited all the day long; remember Thy loving-kindnesses, O Lord, and Thy mercies, which are from everlasting. O remember not the sins of my youth, and of mine ignorance; according to Thy mercy think Thou upon me, O Lord, for Thy goodness’ sake. Gracious and righteous is the Lord, therefore will He give a Law to sinners in the way. He will guide the meek unto judgment, He shall teach the meek His ways. All the paths of the Lord are mercy and truth unto such as keep His covenant, and His testimonies. For Thy Name’s sake, O Lord, be merciful unto my sin, for it is great. What man is he, that feareth the Lord? To him shall He give a Law in the way which He hath chosen. His soul shall dwell at ease, and his seed shall inherit the land. The Lord is the strength of them that fear Him, and He will show them His covenant. Mine eyes are ever toward the Lord, for He shall pluck my feet out of the net. Be charitable unto me, and have mercy on me, for I am only-begotten and poor. The sorrows of my heart are enlarged; O bring Thou me out of my troubles. Look upon my humbleness and my hardship, and forgive all my sins. Consider mine enemies, how many they are, and they bear a tyrannous hate against me. O keep my soul, and deliver me; let me not be confounded, for I have put my trust in Thee. The innocent and the upright have cleaved unto me, for I waited upon Thee, O Lord. Deliver Israel, O God, out of all his troubles.
