Have mercy upon me, O God, according to thy great mercy: according to the multitude of thy tender mercies blot out mine iniquity. Wash me thoroughly from mine iniquity, and cleanse me from my sin. For I acknowledge mine iniquity, and my sin is ever before me. Against thee only have I sinned, and done evil in thy sight: that thou mightest be justified in thy words, and prevail when thou art judged. For behold, I was shapened in iniquity, and in sins did my mother conceive me.  For behold, thou hast loved truth: the unclear and hidden things of thy wisdom thou hast made clear to me. Thou shalt sprinkle me with hyssop, and I shall be clean; thou shalt wash me, and I shall be whiter than snow. Thou shalt make me to hear joy and gladness; the bones which thou hast broken shall rejoice. Turn away thy face from my sins, and blot out all mine iniquities. Create in me a clean heart, O God, and renew a right spirit within me. Cast me not away from thy presence, and take not thy Holy Spirit from me. Restore unto me the joy of thy salvation, and steady me with a guiding spirit.  Then will I teach transgressors thy ways, and the impious shall be converted unto thee. Deliver me from bloodguiltiness, O God, thou God of my salvation, and my tongue shall sing aloud of thy righteousness. O Lord, open thou my lips, and my mouth shall declare thy praise. For hadst thou desired sacrifice, I would have given it thee; thou delightest not in burnt offerings. Sacrifices to God are a contrite spirit: a contrite and humble heart, O God, thou wilt not despise. Do good, O Lord, in thy good will unto Zion, that the walls of Jerusalem may be built up. Then shalt thou be pleased with the sacrifice of righteousness, with burnt offering and whole burnt offerings; Then shall they offer bullocks upon thine altar.
