% source: A Psalter for Prayer
Bow down Thine ear, O Lord, and hear me, for I am poor and in misery. Preserve Thou my soul, for I am holy; save Thy servant, O my God, that putteth his trust in Thee. Have mercy upon me, O Lord, for I will call upon Thee all day. Give joy to the soul of Thy servant, for unto Thee have I lifted up my soul. For Thou, Lord, art good and gentle, and of great mercy unto all them that call upon Thee. Give ear, Lord, unto my prayer, and heed the voice of my supplication. In the day of my trouble I called upon Thee, for Thou hast heard me. Among the gods there is none like unto Thee, O Lord, nor are there any deeds according unto Thy deeds. All nations whom Thou hast made shall come and bow down before Thee, O Lord, and shall glorify Thy Name. For Thou art great, and doest wondrous things; Thou art God alone. Guide me, O Lord, in Thy way, and I will walk in Thy truth; O let my heart rejoice to fear Thy Name. I will thank Thee, O Lord my God, with all my heart, and I will praise Thy Name for evermore. For great is Thy mercy toward me, and Thou hast delivered my soul from the nethermost hell. O God, the wicked are risen against me, and the congregations of the mighty have sought after my soul, and have not set Thee before them. But Thou, O Lord my God, art compassionate and merciful, longsuffering, and greatly charitable and true. O look upon me, and have mercy upon me, give Thy strength unto Thy servant, and help the son of Thine handmaid. Work some sign upon me for good, that they who hate me may see, and be ashamed, because Thou, Lord, hast holpen me, and comforted me.
