% source: A Psalter for Prayer
Lord, Thou hast been our refuge from generation to generation. Before ever the mountains were formed, or the earth and the world were created, even from age to age Thou art. Turn not man away unto humiliation; yea, Thou hast said, Be converted, ye children of men. For a thousand years before Thine eyes, O Lord, are but as yesterday when it is past, and as a watch in the night. Fleeting shall their years be; he shall go by in the morning like the grass; in the morning it shall flourish, and grow up, but in the evening it shall fall away, and dry up, and wither. For we consumed away in Thy displeasure, and were troubled at Thy wrathful indignation. Thou hast set our misdeeds before Thee, our years are in the light of Thy countenance. For all our days are spent, and we have disappeared in Thy wrath; Our years are spun out like a spider’s web. The days of our age are threescore years and ten, or if we be so strong, fourscore years, and more than these is but labor and sorrow; for frailty shall come upon us, and we shall be chastened. Who knoweth the power of Thy wrath, and from fear of Thee, who can recount Thine anger? So make Thy right hand known to me, and to them that are bound by the heart in wisdom. Turn Thee again, O Lord; how long? And be gracious unto Thy servants. We were satisfied with Thy mercy in the morning, O Lord, and we rejoiced and were glad; We were glad all our days; for the days wherein Thou didst humble us, the years wherein we saw adversity. And look upon Thy servants, and upon Thy works, and guide their children, and let the brightness of the Lord our God be upon us, and prosper Thou the work of our hands upon us; yea, prosper Thou our handy-work.
