Glory be to God on high and on earth peace, and good will among men.

We praise Thee, we bless Thee, we give thanks to Thee for Thy great glory.

O Lord, heavenly King, God the Father Almighty; O Lord the Only-begotten Son Jesus Christ, and the Holy Spirit.

O Lord God, Lamb of God, Son of the Father, that takest away the sin of the world, have mercy on us, Thou that takest away the sins of the world.

Receive our prayer, Thou that sittest at the right hand of the Father, have mercy on us.

For Thou only art holy; Thou only art the Lord, O Jesus Christ, to the glory of God the Father. Amen.

Every day will I bless Thee, and I will praise Thy name for ever, yea, for ever and ever.

Lord, Thou hast been our refuge from all generation. I said: Be merciful unto me; heal my soul for I have sinned against Thee.

Lord, I have fled unto Thee, teach me to do Thy will, for Thou art my God.

For with Thee is the fountain of life; in Thy light shall we see light.

O continue Thy lovingkindness unto them that know Thee.

Vouchsafe, O Lord, to keep us this night without sin.

Blessed art Thou, O Lord God of our Fathers, and praised and glorified be Thy name forever. Amen.

Let Thy mercy, O Lord, be upon us, as we do put our hope in Thee.

Blessed art Thou, O Lord, teach me Thy statutes.

Blessed art Thou, O Master, make me to understand thy commandments.

Blessed art Thou, O Holy One, enlighten me with thy precepts.

Thy mercy, O Lord endureth forever: O despise not the works of Thy hands.

To Thee belongeth worship, to Thee belongeth praise, to Thee belongeth glory, to the Father, and to the Son, and to the Holy Spirit, now and ever, and unto ages of ages. Amen.
