\section{Small Compline}

\input{prayers/usualbeginning}

\subsection{Psalm 50}

\input{psalms/50}

\subsection{Psalm 69}

\input{psalms/69}

\subsection{Psalm 142}

\input{psalms/142}

\subsection{The Small Doxology}

\input{prayers/smallDoxology}

\subsection{The Creed}

\input{prayers/creed}

\subsection{Canon}

\rubric{An appropriate akathist hymn, canon, or other prayers may be said here. The service continues with:}

\input{prayers/itIsTrulyMeet}

\subsection{Trisagion}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Kontakion}

\rubric{The appointed kontakion or the apolytikion of the great feast or saint being commemorated is now read. If there is no appointed kontakion or commemoration, the following used:}

O God of our fathers, who ever dealest with us according to thy goodness, remove not thy mercy from us; but by their intercessions direct our lives in peace.

In all the world thy Church, arrayed in the blood of thy martyrs as in purple and fine linen, crieth through them unto thee, O Christ our God: Send down thy compassion upon thy people; give peace to thy commonwealth and to our souls great mercy.

Glory to the Father, and to the Son, and to the Holy Spirit.

With the saints give rest, O Christ, to the souls of thy servants, where there is neither sickness nor sorrow nor sighing but life everlasting.

Both now and ever, and unto ages of ages. Amen.

Through the intercessions of all the saints and of the Theotokos, grant us thy peace, O Lord, and have mercy upon us, for thou alone art compassionate.

\rubric{But on Friday evening, use \unrubric{Unto thee, O Lord the Author of creation} and on Saturday evening, use the hypakoe or resurrectional troparion of the proper tone, which can be found starting on page \pageref{resurrectional}.}

\subsection{Prayer of the Hours}

Lord, have mercy. \rubric{(forty times)}

\input{prayers/hours}

Lord have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian and the Trisagion.}

\input{prayers/stEphraim}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\rubric{The service continues with:}

Lord, have mercy. \rubric{(twelve times)}

\subsection{Prayer of St. Paul of Evergetes}

O spotless, undefiled, incorrupt, immaculate, pure Virgin, Lady Bride of God, who by thy wondrous conceiving hast united God the Word to man, and joined the outcast nature of our race to heavenly things, O only hope of the hopeless, and succor of the embattled, the ready help of them that have recourse to thee, and refuge of all Christians: abhor me not, the sinner, the accursed one, who have altogether made myself unprofitable by shameful thoughts, words, and deeds, and with the heartsease of life's pleasures am become a thrall in mind. But as the Mother of the man-befriending God, do thou, in man-befriending wise, take pity upon me a sinner and prodigal, and receive my supplication, offered thee on unclean lips. And using thy boldness as a mother, entreat thy Son, our Master and Lord, that He may open even unto me the loving compassions of His goodness, and that, overlooking mine innumerable trespasses, He would turn me to repentance, and make me the approved doer of His commandments. And be thou ever with me, as thou art merciful, and compassionate, and the lover of good, being in this life a fervent protectress and help, to defend me from the assaults of adversaries, and guide me unto salvation; and in the hour of my departure, to care for my wretched soul, and drive far from it the dark countenances of evil demons; and in the terrible day of judgment, to deliver me from eternal torment, and show me forth as an heir of the unspeakable glory of thy Son and our God. This be my lot, O my Lady, most holy Theotokos, by thy mediation and help, through the grace and love for man of thine Only-begotten Son, our Lord and God and Savior Jesus Christ, to Whom is due all glory, honor, and worship, with His Father which is without beginning, and His All-holy and good and life-giving Spirit, now and ever, and unto ages of ages. Amen.

\subsection{Prayer of St. Antiochus}

And grant us, O Master, when we go to sleep, repose of body and soul; and keep us from the murky slumbering of sin and every dark voluptuousness of night. Calm the violence of the passions, quench the fiery darts of the evil one, which are treacherously hurled against us. Subdue the rebellions of our flesh, and quell our every earthly and material thought. And grant unto us, O God, a watchful mind, a chaste thought, a sober heart, and sleep light and free from all satanic phantasies. And raise us up at the hour of prayer, established in Thy commandments and holding the remembrance of Thy judgments unshakable within us. Grant us to hymn Thy glory all the night long, that we may praise and bless and glorify Thine all-honored and majestic Name, of the Father, and of the Son, and of the Holy Spirit, now and ever, and unto the ages of ages. Amen.

O most glorious, ever-virgin, blessed Theotokos, present our prayer to thy Son our God, and intercede with him that through thee he may save our souls.

The Father is my Hope; \rubric{(metania)} \\
The Son is my Refuge; \rubric{(metania)} \\
The Holy Spirit is my Protection; \rubric{(metania)}\\
O Holy Trinity: Glory to thee.

In thee, O Mother of God, I place all my hope; keep me under thy protection.

\subsection{Prayer to Our Guardian Angel}

O holy Angel who accompanieth my wretched soul and lowly life, forsake me not, and depart not from me because of my extravagance and wickedness. Give not access to the evil demon to rule with his might this mortal body of mine, but hold me by my wretched, feeble hand; lead me in the path of salvation. Yea, O holy Angel of God, guardian and protector of my wretched soul and body, forgive me all wherewith I have heretofore saddened thee all the days of my life. And though this day I have sinned, be thou my shelter this night. Keep me from all the wiles of the enemy, that I may not anger God with any sin. Intercede with the Lord for me, that he may confirm me in his fear and show me forth as a worthy servant of his goodness. Amen.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
