\section{Confession}

\subsection{What is Sin?}

\begin{itemize} \setlength\itemsep{0pt}
\item Misused gifts of God
\item Anything that keeps us from seeking God with our body, mind, and soul
\item Anything that short-circuits our desire to do as God wants
\item A life without God that is subject to chaos and death
\item Anything experienced in self-interest
\item The sweet enticement of deceit and danger
\end{itemize}

\subsection{Confession Reflection}

\begin{itemize} \setlength\itemsep{0pt}
\item I fail to ask God for Wisdom.
\item I hope not in the Lord.
\item I want justice for others and not myself.
\item Failure to Pray for and Love my enemy.
\item Failure to love my neighbor.
\item Failure to teach my children.
\item Think I am better than others.
\item Judge others and alienate myself from God.
\item Letting others judge me (worry about what they think).
\item Trust in others and not God.
\item Think I can do it on my own.
\item Failure to ask for God's help.
\item Failure to thank God.
\item Am I a thankful person?
\item Easily disturbed or distracted from prayer.
\item Can't say no to things I know I should not do.
\item Think salvation is a decision and not an action.
\item Can't do what I know I should do.
\item Do what I know I should not do.
\item Disrespect my body.
\item Think without listening to my heart.
\item Think I can figure it out.
\item Deny my own pain and faults.
\item Minimize my poor actions.
\item Failure to ask the Holy Spirit for help.
\item Failure to ask God to teach me how to pray.
\item Listen to poor teachers.
\item Thinking that the fast, Eucharist, and confession are unnecessary.
\item Do not think I have to or want to do what God asks.
\item Failure to realize my own faults while identifying those I perceive in others.
\item Boast of my own perceived good.
\item Seek comfort rather than labor for my soul.
\item Separate faith from my actions.
\item Have a poor concept of faith.
\item Do not learn from my mistakes.
\item Blame rather than be responsible for my own actions.
\item Falsely justify my own actions.
\item Don't forgive.
\item Do not ask God to Help Me forgive.
\item I do not take time to listen to God, to be still, to hear the scripture.
\item I am quick to anger.
\item I do not hate my sin.
\item I inappropriately think I am worthless.
\item I am not thankful for the right things.
\item I do not count my trials as something good for me.
\item I do not think and behave well when things go wrong or not the way I think they should.
\item Patience is a distant thing.
\item I have trouble being still.
\item Do I fast with God and give to those in need?
\item Criticism trumps love.
\item I have to be right.
\item Do not believe Jesus is God.
\item Think the Holy Spirit is a force and not a person.
\item Think that human nature is sinful.
\item Avoid prayer, fasting, and confession.
\item Am I sarcastic? Sarcasm is abusive!
\item Do I manipulate others?
\item Do I gossip about others?
\item I do not ask God to teach me.
\item I don't ask God to lead me in the way of peace.
\item I am not kind.
\item I do not share.
\item I want too much of earthly things and not enough of heavenly things.
\item I am not tinderhearted.
\item I do not see myself as slave, as hired servant and as a son of God. (St. Silouan)
\item Do I mourn for the right reasons?
\item Do I weep properly for my shameful deeds and thoughts?
\item Do I waste my time?
\item Do I use my time properly?
\item Do I cling to the past and worry about or live in the future?
\item Do I appreciate creation?
\item Do I remember my guardian angel?
\item Do I turn my back on God?
\item Do I try to trick or deceive God?
\item Do I live in fear?
\item Do I have fears greater than fear of God?
\item Am I poor in spirit?
\item Am I meek? Do I know what it means?
\item Do I hunger and thirst after righteousness?
\item Do I forgive and seed forgiveness?
\item Am I mercifu?
\item Am I pure in heart?
\item Am I a peacemaker?
\item How do I respond to insults?
\item Am I clothed properly with virtue?
\item Do I have the faith/trust of a child?
\item Have I physically hurt others or myself?
\item Death by Envy!
\item Do I ask God:
  \begin{itemize}
  \item to lead me in His way to truth? (Vespers)
  \item to make my heart glad? (Vespers)
  \item to deal with us according to his mercy? (Vespers)
  \item to guide us in his heavenly will? (Vespers)
  \item to enlighten the eyes of our hearts? (Vespers)
  \item to grant our petitions which are to salvation? (Vespers)
  \item that we may do his will knowing that it is good for us? (Vespers)
  \item to open the scripture for us (Liturgy)
  \item for patience?
  \item to guide my steps in the way of peace? (Matins)
  \item that we may see his joy?
  \item to be children of the Light? (Matins)
  \item that we may sing and pray with understanding?
  \item that we may work out our salvation with fear and trembling? (Philippians)
  \item that we may know how to pray as we should? (Matins)
  \item that we may lead a godly life? (Matins)
  \item to blot out our transgressions? (Matins)
  \item to enlighten our mind and guard our senses? (Matins)
  \item to teach us His statues?
  \end{itemize}
\end{itemize}

\subsection{Prayers After Confession}

O almighty and merciful God, I truly thank thee for the forgiveness of my sins; bless me, O Lord, and help me always, that I may ever do that which is pleasing to thee, and sin no more. Amen.

O Lord God of my salvation, the Saviour and Benefactor of my soul, I am truly sorry for my every transgression and I firmly resolve never again to offend thee by my sins, and sincerely promise to amend my way of life. Implant in me the fear of thy blessed commandments, that I may trample down all carnal appetite and may lead a godly life, both thinking and doing always such things as are pleasing unto Thee. I pray thee, grant unto me the Grace of thy Holy Spirit, that thus strengthened, I may shun all evil deeds and works, and words and thoughts, and may avoid all snares of the Evil One. Shine in my heart with the true Sun of thy Righteousness; enlighten my mind and guard all my senses, that walking uprightly in the way of thy statutes, I may attain unto life eternal.  Amen.

O Sovereign Master, who lovest mankind, lead me in thy way, that I may walk in thy truth. Make glad my heart, that I may fear thy Holy Name. O Lord, mighty in mercy, gracious in strength, aid and comfort and save me, as I put my trust in thy holy Name. Rebuke me not, O Lord, in thy displeasure, neither punish me in thy wrath, but show unto me thy great mercy and compassion, O Physician and Healer of my soul. O Merciful Saviour, blot out all my transgressions, for I am heartily sorry for having offended thee. Grant me thy Grace that I may avoid my previous evil ways. Strengthen me, O Mighty One, to withstand those temptations before which I am weak, that I may avoid all future sin. Keep me under thy protection and in the shadow of thy wings, that I may serve thee, praise thee, and glorify thee all the days of my life. Amen.
