\section{Prayers of Intercession}

\subsection{Prayer to One's Patron Saint}

Pray unto God for me, O Holy Saint \rubric{(name of patron saint)}, well-pleasing to God: for I turn unto thee, who art the speedy helper and intercessor for my soul.

\subsection{Prayer to One's Guardian Angel}

O Angel of Christ, holy guardian and protector of my soul and body,
forgive me everything wherein I have offended thee every day of my life,
and protect me from all influence and temptation of the evil one. May I
nevermore anger God by any sin. Pray for me to the Lord, that He may
make me worthy of the grace of the All-holy Trinity, and of the Most
Blessed Theotokos, and of all the Saints. Amen.

\subsection{Another Prayer to One's Guardian Angel}

O holy Angel who accompanieth my wretched soul and lowly life, forsake me not, and depart not from me because of my extravagance and wickedness. Give not access to the evil demon to rule with his might this mortal body of mine, but hold me by my wretched, feeble hand; lead me in the path of salvation. Yea, O holy Angel of God, guardian and protector of my wretched soul and body, forgive me all wherewith I have heretofore saddened thee all the days of my life. And though this day I have sinned, be thou my shelter this night. Keep me from all the wiles of the enemy, that I may not anger God with any sin. Intercede with the Lord for me, that he may confirm me in his fear and show me forth as a worthy servant of his goodness. Amen.

\subsection{General Intercession}

O Lord who lovest mankind, forgive those who hate and wrong us. Do good to those who do good. Grant our brethren and kindred their petitions leading unto salvation and eternal life. Visit the sick and grant them healing. Guide those at sea. Journey with those who travel. Struggle alongside the Orthodox. To those who serve and are kind to us, grant remission of sins.

On Thy servants \rubric{(names of the living)}, and on those who have charged us, unworthy as we are, to pray for them, have mercy according to Thy great mercy. Remember, O Lord, Thy servants \rubric{(names of the departed)}, our fathers and brethren who have fallen asleep, and grant them rest where the light of Thy countenance shines. Remember, O Lord, those who bear fruit and do good works in Thy holy churches and grant them their petitions leading unto salvation and eternal life. Remember also, O Lord, us, Thy humble, sinful and unworthy servants, and enlighten our minds with the light of Thy knowledge, and guide us in the way of Thy commandments, by the prayers of our immaculate Lady, the Theotokos, and Ever-Virgin Mary, and of all Thy Saints, for Thou art blessed to the ages of ages. Amen. 

\cleardoublepage

\subsection{Living}

\cleardoublepage

\subsection{Departed}

\cleardoublepage
