\section{Simplified Midnight Office}

\input{prayers/usualBeginning}

\subsection{Psalm 50}

\input{psalms/50}

\subsection{Psalm 120}

\input{psalms/120}

\subsection{Psalm 133}

\input{psalms/133}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Alleluia, alleluia, alleluia. Glory to thee, O God. \rubric{(thrice)}

Lord, have mercy. \rubric{(thrice)}

\subsection{Troparia to the Holy Trinity}

Having arisen from sleep, we fall down before thee, O Blessed One, and sing to thee, O Mighty One, the Angelic Hymn: Holy, holy, holy art thou, O God. Through the Theotokos have mercy on us.

Glory to the Father, and to the Son, and to the Holy Spirit:

From my bed and sleep Thou hast raised me: O Lord, enlighten my mind and my heart, and open my lips that I may praise thee, O Holy Trinity: Holy, holy, holy art thou, O God. Through the Theotokos have mercy on us.

Both now and ever, and unto ages of ages. Amen.

Suddenly the Judge shall come, and the deeds of each shall be revealed: but with fear we cry out in the middle of the night: Holy, holy, holy art thou, O God. Through the Theotokos have mercy on us.

\subsection{Prayer to the Holy Trinity}

Arising from sleep I thank thee, O holy Trinity, because of the abundance of thy goodness and longsuffering thou wast not wroth with me, slothful and sinful as I am; neither hast thou destroyed me in my transgressions: but in thy compassion raised me up, as I lay in despair; that at dawn I might sing the glories of thy Majesty. Do thou now enlighten the eyes of my understanding, open my mouth to receive thy words, teach me thy commandments, help me to do thy will, confessing thee from my heart, singing and praising thine All-holy Name: of the Father, and of the Son, and of the Holy Spirit: now and ever, and unto ages of ages. Amen.

\subsection{The Creed}

\input{prayers/creed}

\subsection{A Prayer of St. Basil}

We bless thee, O God most high and Lord of mercies, who ever workest great and mysterious deeds for us, glorious, wonderful, and numberless; who providest us with sleep as a rest from our infirmities and as a repose for our bodies tired by labor. We thank thee that thou hast not destroyed us in our transgressions, but in thy love toward mankind thou hast raised us up, as we lay in despair, that we may glorify thy Majesty. We entreat thine infinite goodness, enlighten the eyes of our understanding and raise up our minds from the heavy sleep of indolence; open our mouths and fill them with thy praise, that we may unceasingly sing and confess thee, who art God glorified in all and by all, the eternal Father, the Only-Begotten Son, and the all-holy and good and life-giving Spirit: now and ever, and unto ages of ages. Amen.
%\enlargethispage{-2\baselineskip} % Widow prevention

O most glorious, ever-virgin, blessed Theotokos, present our prayer to thy Son our God, and intercede with him that through thee he may save our souls.

The Father is my Hope; \rubric{(metania)}\\
The Son is my Refuge; \rubric{(metania)}\\
The Holy Spirit is my Protection; \rubric{(metania)}\\
O Holy Trinity: Glory to thee.

In thee, O Mother of God, I place all my hope; keep me under thy protection.

It is truly meet to bless thee, O Theotokos, ever blessed and all-blameless, and the mother of our God. More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

O Lord who lovest mankind, forgive those who hate and wrong us. Do good to those who do good. Grant our brethren and kindred their petitions leading unto salvation and eternal life. Visit the sick and grant them healing. Guide those at sea. Journey with those who travel. Struggle alongside the Orthodox. To those who serve and are kind to us, grant remission of sins.

On Thy servants \rubric{(names of the living)}, and on those who have charged us, unworthy as we are, to pray for them, have mercy according to Thy great mercy. Remember, O Lord, Thy servants \rubric{(names of the departed)}, our fathers and brethren who have fallen asleep, and grant them rest where the light of Thy countenance shines. Remember, O Lord, those who bear fruit and do good works in Thy holy churches and grant them their petitions leading unto salvation and eternal life. Remember also, O Lord, us, Thy humble, sinful and unworthy servants, and enlighten our minds with the light of Thy knowledge, and guide us in the way of Thy commandments, by the prayers of our immaculate Lady, the Theotokos, and Ever-Virgin Mary, and of all Thy Saints, for Thou art blessed to the ages of ages. Amen. 

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian.}

\input{prayers/stEphraim}

\rubric{Lastly, we say:}

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
