\section{Ninth Hour}

\input{prayers/usualbeginning}

\subsection{Psalm 83}

\input{psalms/83}

\subsection{Psalm 84}

\input{psalms/84}

\subsection{Psalm 85}

\input{psalms/85}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Alleluia, alleluia, alleluia. Glory to thee, O God. \rubric{(thrice)}

Lord, have mercy. \rubric{(thrice)}

\subsection{Troparia and Verses}

\rubric{If it is a weekday of Great Lent, the following troparia and verses are sung in Tone 8, else we say \unrubric{Glory...}, the troparion of the day, then \unrubric{Both now...}. The troparion of the day can be found starting on page \pageref{weekday}.}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

O thou, who at the ninth hour, for our sake didst taste death in the flesh: Mortify thou the pride of our flesh, and save us, O Christ God. \rubric{(prostration)}

\rubric{Verse 1:} Let my supplication draw nigh before thee, O Lord; according to thine oracle give me understanding. \rubric{(prostration)}

\rubric{Verse 2:} Let my petition come before thee, O Lord: according to thine oracle deliver me. \rubric{(prostration)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\subsection{Theotokion and Psalm Verses}

Thou who for our sake wast born of a virgin and didst suffer crucifixion, O good One, and didst despoil death through death and as God didst reveal resurrection: Despise not those whom thou hast created with thine own hand; show forth thy love for mankind, O merciful One; accept the intercession of thy mother, the Theotokos, for us, and save thy despairing people, O our Savior.

Deliver us not up utterly, for thy holy name's sake, neither disannul thou thy covenant, and cause not thy mercy to depart from us, for Abraham's sake, thy beloved, and for Isaac's sake, thy servant, and for Israel's, thy holy one. 

\subsection{Trisagion}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Kontakion}

\rubric{The kontakion of the day can be found starting on page \pageref{weekday} for weekdays. If it is Great Lent, say:}

When the thief beheld the Author of life hanging upon the cross, he said: If thou wert not god, who art here crucified with us, then had the sun not veiled its rays, neither would the earth have shaken with trembling. But do thou, who sufferest for all men, remember me, O Lord, when thou comest in thy kingdom.

Glory to the Father, and to the Son, and to the Holy Spirit.

In the midst, between two thieves, was thy cross found, the balance-beam of righteousness; for while the one was led down to hades by the heaviness of his blaspheming, the other was lightened of his sins, unto the knowledge of things divine, O Christ God, glory to thee.

Both now and ever, and unto ages of ages. Amen.

When she who bare thee beheld upon the cross thee, the Lamb and Shepherd and Savior of the world, she weeping said: The world rejoiceth, in that it hath received redemption, but my inward parts are inflamed as I behold thy crucifixion, which thou sufferest for all men, O my Son and my God.

\rubric{But on Saturday, use \unrubric{Unto thee, O Lord the Author of creation} and on Sunday, use the hypakoe of the proper tone, which can be found starting on page \pageref{resurrectional}.}

\subsection{Prayer of the Hours}

Lord, have mercy. \rubric{(forty times)}

O Christ our God, who at all times and in every hour, in heaven and on earth, art worshiped and glorified; who art longsuffering, merciful and compassionate; who lovest the just and showest mercy upon the sinner; who callest all to salvation through the promise of blessings to come; O Lord, in this hour receive our supplications, and direct our lives according to thy commandments. Sanctify our souls, hallow our bodies, correct our thoughts, cleanse our minds; deliver us from all tribulation, evil and distress. Encompass us with thy holy Angels, that guided and guarded by them, we may attain to the unity of the faith and to the knowledge of thine unapproachable glory, for thou art blessed unto ages of ages. Amen.

Lord have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian and the Trisagion.}

\input{prayers/stEphraim}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

\subsection{The Final Prayer}

O Master, Lord Jesus Christ our God, who art longsuffering toward our sins and who hast led us even to the present hour, in which, as thou didst hang upon the life-giving tree thou didst make a way into paradise for the penitent thief and by death didst destroy death: Be gracious unto us sinners and thine unworthy servants; for we have sinned and have dealt iniquitously, and we are not worthy to lift up our eyes and look upon the heights of heaven, inasmuch as we have departed from the path of thy righteousness and have walked after the desires of our own hearts. But we implore of thy boundless goodness: Spare us, O Lord, according to the multitude of thy mercy, and save us, for thy holy name's sake; for our days have passed away in vanity. Wrest us out of the hand of the adversary, and forgive our sins, and mortify our carnal imagination, that, putting off the old man, we may be clothed upon with the new man and may live unto thee, our Master and our Benefactor, and that, so following after thy commandments, we may attain unto rest eternal, where is the abode of all those who rejoice. For thou art, in verity, the true Joy and Exultation of those who love thee, O Christ our God, and unto thee we ascribe glory, together with thine unoriginate Father and thine all-holy and good and life-giving Spirit, now and ever, and unto ages of ages. Amen.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
