\section{The Six Psalms and Orthros Prayers}

\subsection{Psalm 3}

Lord, how are they increased that trouble me! Many are they that rise up against me. Many there be which say of my soul, There is no help for him in God. But thou, O Lord, art a shield for me; my glory, and the lifter up of mine head. I cried unto the Lord with my voice, and he heard me out of his holy hill. I laid me down and slept; I awaked; for the Lord sustained me. I will not be afraid of ten thousands of people, that have set themselves against me round about. Arise, O Lord; save me, O my God: for thou hast smitten all mine enemies upon the cheek bone; thou hast broken the teeth of the ungodly. Salvation belongeth unto the Lord: thy blessing is upon thy people.

\subsection{Psalm 37}

O Lord, rebuke me not in thy wrath: neither chasten me in thy hot displeasure. For thine arrows stick fast in me, and thy hand presseth me sore. There is no soundness in my flesh because of thine anger; neither is there any rest in my bones because of my sin. For mine iniquities are gone over mine head: as an heavy burden they are too heavy for me. My wounds stink and are corrupt because of my foolishness. I am troubled; I am bowed down greatly; I go mourning all the day long. For my loins are filled with a loathsome disease: and there is no soundness in my flesh. I am feeble and sore broken: I have roared by reason of the disquietness of my heart. Lord, all my desire is before thee; and my groaning is not hid from thee. My heart panteth, my strength faileth me: as for the light of mine eyes, it is also gone from me. My lovers and my friends stand aloof from my sore; and my kinsmen stand afar off. They also that seek after my life lay snares for me: and they that seek my hurt speak mischievous things, and imagine deceits all the day long. But I, as a deaf man, heard not; and I was as a dumb man that openeth not his mouth. Thus I was as a man that heareth not, and in whose mouth are no reproofs. For in thee, O Lord, do I hope: thou wilt hear, O Lord my God. For I said, Hear me, lest otherwise they should rejoice over me: when my foot slippeth, they magnify themselves against me. For I am ready to halt, and my sorrow is continually before me. For I will declare mine iniquity; I will be sorry for my sin. But mine enemies are lively, and they are strong: and they that hate me wrongfully are multiplied. They also that render evil for good are mine adversaries; because I follow the thing that good is. Forsake me not, O Lord: O my God, be not far from me. Make haste to help me, O Lord my salvation.

\subsection{Psalm 62}

O God, thou art my God; early will I seek thee: my soul thirsteth for thee, my flesh longeth for thee in a dry and thirsty land, where no water is; to see thy power and thy glory, so as I have seen thee in the sanctuary. Because thy lovingkindness is better than life, my lips shall praise thee. Thus will I bless thee while I live: I will left up my hands in thy name. My soul shall be satisfied as with marrow and fatness; and my mouth shall praise thee with joyful lips: when I remember thee upon my bed, and meditate on thee in the night watches. Because thou hast been my help, therefore in the shadow of thy wings will I rejoice. My soul followeth hard after thee: thy right hand upholdeth me. But those that seek after my soul, to destroy it, shall go into the lower parts of the earth. They shall fall by the sword: they shall be a portion for foxes. But the king shall rejoice in God; everyone that sweareth by him shall glory: but the mouth of them that speak lies shall be stopped.

\subsection{Psalm 87}

O Lord God of my salvation, I have cried day and night before thee: let my prayer come before thee: incline thine ear unto my cry; for my soul is full of troubles: and my life draweth nigh unto the grave. I am counted with them that go down into the pit: I am as a man that hath no strength: free among the dead, like the slain that lie in the grave, whom thou rememberest no more: and they are cut off from thy hand. Thou hast laid me in the lowest pit, in darkness, in the deeps. Thy wrath lieth hard upon me, and thou hast afflicted me with all thy waves. Thou hast put away mine acquaintance far from me: thou hast made me an abomination unto them: i am shut up, and I cannot come forth. Mine eye mourneth by reason of affliction: Lord, I have called daily upon thee, I have stretched out my hands unto thee. Wilt thou shew wonders to the dead? shall the dead arise and praise thee? Shall thy lovingkindess be declared in the grave? or thy faithfulness in destruction? Shall thy wonders be known in the dark? and thy righteousness in the land of forgetfulness? But unto thee have I cried, O Lord; and in the morning shall my prayer come before thee. Lord, why castest thou off my soul? why hidest thou thy face from me? I am afflicted and ready to die from my youth up: while I suffer thy terrors I am distracted. Thy fierce wrath goeth over me: thy terrors have cut me off. They came round about me daily like water; they compassed me about together. Lover and friend hast thou put far from me, and mine acquaintance into darkness.

\subsection{Psalm 102}

Bless the Lord, O my soul: and all that is within me, bless his holy name. Bless the Lord, O my soul, and forget not all his benefits: who forgiveth all thine iniquities; who healeth all thy diseases; who redeemeth thy life from destruction; who crowneth thee with lovingkindness and tender mercies; who satisfieth thy mouth with good things; so that thy youth is renewed like the eagle's. The Lord executeth righteousness and judgment for all that are oppressed. He made known his ways unto Moses, his acts unto the children of Israel. The Lord is merciful and gracious, slow to anger, and plenteous in mercy. He will not always chide: neither will he keep his anger forever. He hath not dealt with us after our sins; nor rewarded us according to our iniquities. For as the heaven is high above the earth, so great is his mercy toward them that fear him. As far as the east is from the west, so far hath he removed our transgressions from us. Like as a father pitieth his children, so the Lord pitieth them that fear him. For he knoweth our frame; he remembereth that we are dust. As for man, his days are as grass: as a flower of the field, so he flourisheth. For the wind passeth over it, and it is gone; and the place thereof shall know it no more. But the mercy of the Lord is from everlasting to everlasting upon them that fear him, and his righteousness unto children's children; to such as keep his covenant, and to those that remember his commandments to do them. The Lord hath prepared his throne in the heavens; and his kingdom ruleth over all. Bless the Lord, ye his angels, that excel in strength, that do his commandments, hearkening unto the voice of his word. Bless ye the Lord, all ye his hosts; ye ministers of his, that do his pleasure. Bless the Lord, all his works in all places of his dominion: bless the Lord, O my soul.

\subsection{Psalm 142}

Hear my prayer, O Lord, give ear to my supplications: in thy faithfulness answer me, and in thy righteousness. And enter not into judgment with thy servant: for in thy sight shall no man living be justified. For the enemy hath persecuted my soul; he hath smitten my life down to the ground; he hath made me to dwell in darkness, as those that have been long dead. Therefore is my spirit overwhelmed within me; my heart within me is desolate. I remember the days of old; I meditate on all thy works; I muse on the work of thy hands. I stretch forth my hands unto thee: my soul thirsteth after thee, as a thirsty land. Hear me speedily, O Lord: my spirit faileth: hide not thy face from me, lest I be like unto them that go down into the pit. Cause me to hear thy lovingkindness in the morning; for in thee do I trust: cause me to know the way wherein I should walk; for I lift up my soul unto thee. Deliver me, O Lord, from mine enemies: I flee unto thee to hide me. Teach me to do thy will; for thou art my God: thy spirit is good; lead me into the land of uprightness. Quicken me, O Lord, for thy name's sake: for thy righteousness' sake bring my soul out of trouble. And of thy mercy cut off mine enemies, and destroy all them that afflict my soul: for I am thy servant.

\subsection{The Twelve Orthros Prayers}

\rubric{(1.)} We give thanks unto thee, O Lord our God, who hast raised us up from our beds and hast put into our mouths a word of praise, that we may worship and call upon thy holy name. And we entreat thee, by thy mercies which thou hast exercised always in our life, send down now also thine aid upon those who stand before the face of thy holy glory and await the rich mercy which is from thee. And grant that they may always, with fear and love, adore thee, praise thee, hymn thee and worship thine inexpressible goodness. For unto thee are due all glory, honor and worship to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(2.)} Out of the night our spirit awaketh at dawn unto thee, O our God; for thy commandments are a light upon the earth. Teach us to perfect righteousness and holiness in thy fear; for we glorify thee, our God, who dost truly exist. Incline thine ear, and hear us, and be mindful, O Lord of the names of all those who are with us and pray with us, and save them by thy might. Bless thy people, and sanctify thine inheritance. Give peace to thy world, to thy churches, to the priests, to all civil authorities and all thy people. For blessed and glorified is thine all-honorable and majestic name of the Father and of the Son and of the Holy Spirit, now and ever and unto ages of ages. Amen.

\rubric{(3.)} Out of the night our spirit awaketh at dawn unto thee, O God; for thy commandments are a light. Teach us thy righteousness, thy commandments and thy statues, O God. Enlighten the eyes of our understanding lest at any time we sleep unto death in sins. Dispel all darkness from our hearts. Graciously give unto us the Sun of righteousness, and by thy Holy Spirit preserve our life unassailed. Guide our steps into the way of peace. Grant us to behold the dawn and the day with joy, that we may raise our morning prayers unto thee. For thine is the might, and thine is the kingdom and the power and the glory of the Father and of the Son and of the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(4.)} O Master God, holy and unsearchable, who didst command the light to shine forth from the darkness, who hast refreshed us by the slumber of the night and hast raised us up to glorify and supplicate thy goodness: Being implored of thine own tender loving-kindness, receive us also now who worship thee and render thanks unto thee according to the measure of our strength; and grant us all our petitions which are unto salvation. Make us sons of the light and of the day and heirs of thine everlasting good things. Be mindful, O Lord, in the multitude of thy mercies, of all thy people here present with us and who pray with us and all our brethren on land, on the sea, in the air and in every place of thy dominion, who are in need of thy love for mankind and of thy help, and grant unto all thy great mercy, that being preserved in safety of soul and body, we may with boldness magnify thy wondrous and blessed name of the Father and of the Son and of the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(5.)} O Treasury of good things, Fountain eternal, O holy Father who workest wonders, allpowerful and almighty: We worship thee and pray thee, calling thy mercies and thy compassions to the aid and defense of our lowliness. Be mindful of thy servants, O Lord; receive the morning prayers of us all as incense before thee; and let none of us be found reprobate, but encompass us with thy compassions. Be mindful, O Lord, of those who watch and sing to the glory of thine only-begotten Son, who is our God, and thy Holy Spirit. Be thou their Helper and their Support. Receive thou their supplications upon thy most heavenly and ideal altar. For thou art our God, and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(6.)} We give thanks unto thee, O Lord God of our salvation; for thou doest all things which are for the welfare of our souls, that we may ever look upward unto thee, the Saviour and Benefactor of our souls. For thou hast refreshed us in that part of the night which is past and hast raised us up from our beds and hast led us to stand here in worship of thy precious name. Wherefore we entreat thee, O Lord, give us grace and power, that we may be vouchsafed with understanding to sing praise unto thee and to pray without ceasing, in fear and trembling working out our own salvation, through the help of thy Christ. Be mindful, O Lord, of those who cry aloud unto thee in the night; hearken unto them, and have mercy, and crush under their feet invisible and warring enemies. For thou art the King of peace and the Saviour of our souls, and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(7.)} O God and Father of our Lord Jesus Christ, who hast raised us up from our beds and hast gathered us together at this hour of prayer: Grant us grace in the opening of our mouth, and receive our thanksgivings as we have power to make them, and instruct us in thy statutes. For we know not how to pray as we ought unless thou, O Lord, by thy Holy Spirit, dost guide us. Wherefore, we beseech thee: Forgive, remit, pardon whatsoever sins we may have committed unto this present hour, whether by word or deed or thought, whether voluntarily or involuntarily; for if thou wilt be extreme to mark iniquity, O Lord, Lord, who shall stand? For with thee is redemption. For thou only art holy, a mighty Helper and the Defender of our life, and our song shall ever be of thee. Blessed and glorified be the might of thy kingdom of the Father and of the Son and of the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(8.)} O Lord our God, who hast banished from us the sluggishness of sleep and hast called us together by a holy bidding, that in the night also we may lift up our hands and confess thy righteous judgments: Receive our prayers, petitions, confessions and nocturnal adoration and grant unto us, O God, faith unashamed, hope unwavering, love unfeigned. Bless our comings and our goings, our deeds and works and words and thoughts. And grant that we may come to the beginning of this day praising, singing and blessing the goodness of thine ineffable beneficence. For blessed is thine all-holy name, and glorified is thy kingdom of the Father and of the Son and of the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(9.)} Illumine our hearts, O Master who lovest mankind, with the pure light of thy divine knowledge, and open the eyes of our mind to the understanding of thy gospel teachings; implant in us also the fear of thy blessed commandments, that trampling down all carnal desires, we may enter upon a spiritual manner of living, both thinking and doing such things as are well-pleasing unto thee. For thou art our Sanctification and Illumination, and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(10.)} O Lord our God, who hast granted unto men pardon through repentance and hast set for us the repentance of the prophet David as an example of the acknowledgement of sin and of confession which is unto forgiveness: Do thou thyself, O Master, have mercy on us according to thy great mercy, notwithstanding the manifold and great iniquities into which we have fallen; and according to the multitude of thy compassions, blot out our transgressions. Against thee have we sinned, O Lord, thou who knowest the hidden and secret things in the heart of men and who alone hast power to forgive sins; and as thou hast created a clean heart within us and established us with thy governing Spirit and made known unto us the joy of thy salvation, cast us not away from thy presence. But inasmuch as thou art good and lovest mankind, graciously vouchsafe that even until our uttermost breath, we may offer unto thee the sacrifice of righteousness and an oblation upon thy holy altar. Through the mercy and compassions and love for mankind of thine only-begotten Son, with whom thou art blessed, together with thine all-holy and good and life-giving Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(11.)} O God, our God, who hast brought into being by thy will all the powers endowed with speech and reason, we pray thee and supplicate thee: Receive our praise, which together with all thy creatures we offer according to our strength, and reward us with the rich gifts of thy goodness. For unto thee every knee doth bow, whether in heaven or on earth or in the regions under the earth, and every breath and created being doth sing thine ineffable glory, for thou only art the true and most merciful God. For all the powers of heaven praise thee, and unto thee they ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.

\rubric{(12.)} We praise thee, we hymn thee, we bless thee, we give thanks unto thee, O God of our fathers, that thou hast brought us in safety through the shades of night and hast shown unto us once again the light of day. And we entreat of thy goodness: Be gracious unto our sins, and receive our prayer in thy great tenderness. For we flee unto thee, the merciful and almighty God. Illumine our hearts with the true Sun of thy righteousness; enlighten our mind and guard all our senses, that walking uprightly as in the day, in the way of thy commandments, we may attain unto life eternal, for with thee is the fountain of life, and may graciously be vouchsafed to come unto the fruition of the light unapproachable. For thou art our God, and unto thee we ascribe glory to the Father and to the Son and to the Holy Spirit, now and ever, and unto ages of ages. Amen.
