\section{Preparing to Worship}

\subsection{Trisagion Prayers}

In the Name of the Father, and of the Son, and of the Holy Spirit. Amen.

Glory to thee, our God, glory to thee.

O heavenly King, O Comforter, the Spirit of truth, who art in all places and fillest all things; Treasury of good things and Giver of life: Come and dwell in us and cleanse us from every stain, and save our souls, O gracious Lord.

Holy God, Holy Mighty, Holy Immortal: have mercy on us. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever and unto ages of ages. Amen.

All-holy Trinity, have mercy on us. Lord, cleanse us from our sins. Master, pardon our iniquities. Holy God, visit and heal our infirmities for thy Name's sake.

Lord, have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Our Father, who art in heaven, hallowed be thy Name; thy kingdom come; thy will be done on earth, as it is in heaven. Give us this day our daily bread; and forgive us our trespasses, as we forgive those who trespass against us; and lead us not into temptation, but deliver us from evil.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Prayer on Entering the Church}

    By the multitude of Thy mercy I will come into Thine house; in Thy fear will I worship toward Thy holy temple. Lead me, O Lord, in Thy righteousness; because of mine enemies, make my way plain before Thee, that with a clear mind I may glorify thee forever, One Divine Power worshiped in three persons: Father, Son, and Holy Spirit. Amen. 

\subsection{Prayer Before the Icon of Christ}

    We reverence thy spotless Icon, O gracious Lord, and ask forgiveness of our transgressions, O Christ our God: for of thine own good will thou wast pleased to ascend the Cross in the flesh, that thou mightest deliver from bondage to the enemy those whom thou hadst fashioned. Wherefore, we cry aloud unto thee: thou hast filled all things with joy, O our Savior, for thou didst come to save the world.

\subsection{Prayer Before the Icon of the Theotokos}

    Forasmuch as thou art a well-spring of tenderness, O Theotokos, make us worthy of compassion; Look upon a sinful people; Manifest thy power as ever, for hoping on thee we cry aloud unto thee: Hail! as once did Gabriel, Chief Captain of the Bodiless Powers.
    
\subsection{Prayer Before Reading Scripture}

Illumine our hearts, O Master who lovest mankind, with the pure light of thy divine knowledge, and open the eyes of our mind to the understanding of thy gospel teachings; implant in us also the fear of thy blessed commandments, that trampling down all carnal desires, we may enter upon a spiritual manner of living, both thinking and doing such things as are well-pleasing unto thee. For thou art the Illumination of our souls and bodies, O Christ our God, and unto thee we ascribe glory, together with thine unoriginate Father and thine all-holy and good and life-giving Spirit, now and ever, and unto ages of ages. Amen.

\subsection{A Prayer Before Reading Spiritual Texts}

O Lord Jesus Christ, open the eyes of my heart, that I may hear thy word and that I may understand and do thy will, for I am a sojourner upon the earth. Hide not thy commandments from me, but open my eyes, that I may perceive the wonders of thy law. Reveal to me the hidden and secret lore of thy wisdom. In thou, O God, do I place my hope. Enlighten my mind and understanding with the light of thy knowledge, not only to cherish those things that are written, but to do them; that in reading the lives and sayings of the saints I may not sin, but that such may serve for my renewal, enlightenment, and sanctification, for the salvation of my soul and the inheritance of everlasting life. For thou art the enlightenment of those who lie in darkness, and from thee cometh every good deed and every gift.
Amen.

\subsection{A Prayer Before Singing}

O Lord, strengthen me to concentrate attentively on the words I pronounce. Grant that these words may come from the depth of my soul. May the vivifying grace of the Holy Spirit pour into the hearts of those who hear our song.

May our prayers become a sweet spiritual fragrance that rises before Thee for all mankind, filled with hope and love for Thee. Grant that we who praise Thee may be united by Thy Holy Spirit in a bond of love, that with one mouth and one heart we might praise, bless, and worship Thee, the Light above all Lights, the True Life, and the Salvation of our souls. Amen.

\cleardoublepage
