\section{First Hour}

\input{prayers/usualBeginning}

\subsection{Psalm 5}

\input{psalms/5}

\subsection{Psalm 89}

\input{psalms/89}

\subsection{Psalm 100}

\input{psalms/100}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Alleluia, alleluia, alleluia. Glory to thee, O God. \rubric{(thrice)}

Lord, have mercy. \rubric{(thrice)}

\subsection{Troparia and Verses}

\rubric{If it is a weekday of Great Lent, the following troparia and verses are sung in Tone 6, else we say \unrubric{Glory...}, the troparion of the day, then \unrubric{Both now...}. The troparion of the day can be found starting on page \pageref{weekday}.}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

In the morning attend unto the voice of my supplication, O my King and my God. \rubric{(prostration)}

\rubric{Verse 1:} Unto my words give ear, O Lord; hear my cry. \rubric{(prostration)}

\rubric{Verse 2:} For unto thee will I pray, O Lord: thou shalt hearken in the morning to my voice. \rubric{(prostration)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\subsection{Theotokion and Psalm Verses}

What shall I call thee, O thou who art full of grace? Heaven, for from thee shone forth the Sun of righteousness; Paradise, for thou hast budded forth the Flower of immortality; Virgin, for thou hast remained incorrupt; Pure Mother, for thou hast held in thy holy embrace a Son, who is God of all. Beseech thou him to save our souls.

My steps do thou direct according to thy saying, and so let no iniquity have dominion over me. \rubric{(twice in Lent)}

Deliver me from the false accusation of men, and I will keep thy commandments. \rubric{(twice in Lent)}

Make thy face to shine upon thy servant, and teach me thy statutes. \rubric{(twice in Lent)}

Let my mouth be filled with thy praise, O Lord, that I may hymn thy glory and thy majesty all the day long. \rubric{(thrice in Lent)}

\subsection{Trisagion}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Kontakion}

\rubric{The kontakion of the day can be found starting on page \pageref{weekday}. If it is Great Lent, use the following kontakia:}

\rubric{Monday, Tuesday, Thursday:} With hearts and mouths let us continually magnify the glorious Mother of God, more holy than the angels, confessing her to be the Theotokos, who did, in very truth, bring forth God incarnate and who unceasingly doth intercede for our souls.

\rubric{Wednesday, Friday:} Quickly go before us, O Christ our God, lest the enemy which blasphemeth thee and constraineth us, lead us into captivity. Overcome by the cross those who war against us, that they may know what power hath the faith of Orthodox believers; through the intercessions of the Theotokos, O thou who alone lovest mankind.

\rubric{Saturday:} Unto thee, O Lord, the Author of creation, the universe doth offer the God-bearing martyrs as the first-fruits of nature. By whose prayers, through the Theotokos, do thou preserve thy Church in profound peace, O most merciful One.

\rubric{On Sunday, use the hypakoe of the proper tone, which can be found starting on page \pageref{resurrectional}.}

\subsection{Prayer of the Hours}

Lord, have mercy. \rubric{(forty times)}

\input{prayers/hours}

Lord have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\input{prayers/moreHonorable}

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian and the Trisagion.}

\input{prayers/stEphraim}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

\subsection{The Final Prayer}

O Christ, the true Light, which illumineth and sanctifieth every man who cometh into the world: Let the light of thy countenance be signed upon us, that in it we may behold the light unapproachable. Guide our footsteps aright, to the keeping of thy commandments, through the intercessions of thine all-immaculate Mother and of all thy saints. Amen.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
