\section{Resurrectional Hymns in the Eight Tones} \label{resurrectional}

\subsection{Tone One}

\subsubsection{Apolytikion}

While the stone was sealed by the Jews, and the soldiers were guarding Thy most pure body, Thou didst arise on the third day, O Savior, granting life to the world. For which cause the heavenly powers cried aloud unto Thee, O giver of life. Glory to Thy Resurrection O Christ, glory to Thy kingdom, glory to Thy providence, O Thou Who alone art the lover of mankind.

\subsubsection{Theotokion}

As Gabriel cried aloud unto thee, “Hail, O Virgin,” with that cry did the Lord of all become incarnate in thee, O holy ark, as spake the righteous David; and Thou wast revealed as more spacious than the heavens, in that thou bore thy Creator. Wherefore, glory to Him Who abode in thee; glory to Him Who came from thee; glory to Him, Who through thy birth-giving hath set us free.

\subsubsection{Kontakion}

As God, Thou didst rise in glory from the grave, raising the world with Thee. All nature doth praise Thee as God. Death is destroyed and Adam doth rejoice, O Master, whilst Eve, now freed from bondage, doth rejoice, saying: Thou it is, O Christ, Who granteth Resurrection to all.

\subsubsection{Hypakoe}

The repentance of the thief gained him paradise by stealth, and the sighing of the ointment-bearing women proclaimed the glad tidings that Thou wast risen, O Christ, and hadst bestowed upon the world Thy Great Mercy.

\subsection{Tone Two}

\subsubsection{Apolytikion}

When Thou didst submit Thyself unto death, O Thou deathless and immortal One, then Thou didst destroy hell with Thy Godly power. And when Thou didst raise the dead from beneath the earth, all the powers of Heaven did cry aloud unto Thee: O Christ, Thou giver of life, glory to Thee.

\subsubsection{Theotokion}

Exceeding glorious beyond the power of thought are thy mysteries, O Theotokos. For being sealed in purity and preserved in virginity, thou wast acknowledged to be in very truth the mother who didst bring forth the true God; wherefore entreat Him to save our souls.

\subsubsection{Kontakion}

Thou didst arise from the grave, O Almighty Savior, and Hades seeing the miracle wast astonished, and the dead arose. Creation doth see this and doth rejoice with Thee, whilst Adam joins in exaltation, and the world doth praise Thee forever, O my Savior.

\subsubsection{Hypakoe}

The women went to the tomb after Thy passion to anoint Thy body, O Christ God, where they saw a vision of angels, and were astonished; for they heard them crying with a loud voice, The Lord is risen and hath granted the world Great Mercy.

\subsection{Tone Three}

\subsubsection{Apolytikion}

Let the heavens rejoice and the earth be glad, for the Lord hath done a mighty act with His own arm. He hath trampled down death by death, and become the first-born from the dead. He hath delivered us from the depths of Hades, granting the world the Great Mercy.

\subsubsection{Theotokion}

Thee, who art the mediatrix for the salvation of our race, we praise, O Virgin Theotokos; for in the flesh assumed from thee, after that He had suffered the passion of the Cross, thy Son and our God delivered us from corruption, because He is the Lover of mankind.

\subsubsection{Kontakion}

Today, Thou didst arise from the grave, O merciful Lord, and Thou didst extract us from the gates of death. Today, Adam dances and Eve rejoices. With them the prophets and patriarchs unceasingly praise the divine might of Thy Kingdom.

\subsubsection{Hypakoe}

To the ointment-bearing women the brilliant angel of sweet words, startling them, did say: Why seek ye the living One in the grave? He is verily risen, and hath emptied the tombs. Know ye, therefore, that the changeless One hath changed corruption to incorruption. And say to God: How dreadful are Thy works; for Thou hast saved mankind.

\subsection{Tone Four}

\subsubsection{Apolytikion}

Having learned the joyful message of the Resurrection from the angel the women disciples of the Lord cast from them their parental condemnation. And proudly broke the news to the Disciples, saying: Death hath been spoiled; Christ God is risen, granting the world Great Mercy.

\subsubsection{Theotokion}

The Mystery which was hidden from everlasting and was unknown of the angels, O Theotokos, was revealed through thee, to those who dwell upon earth. In that God, having become incarnate in unconfused union of His own good will accepted the Cross for our sake. Whereby He raised again the first created, and hath saved our souls from death.

\subsubsection{Kontakion}

My Savior and Redeemer, as God Thou hast raised from the grave all those who were in chains, and hast shattered the gates of Hades. As Lord, Thou didst arise on the third day.

\subsubsection{Hypakoe}

The ointment-bearing women hastened running to the Apostles and related to them the account of Thy Resurrection, O Christ, saying, Thou hast risen because Thou art God, granting the world Great Mercy.

\subsection{Tone Five}

\subsubsection{Apolytikion}

Let us believers praise and worship the Word; coeternal with the Father and the Spirit, born of the Virgin for our salvation. For, He took pleasure in ascending the Cross in the flesh to suffer death; and to raise the dead by His glorious Resurrection.

\subsubsection{Theotokion}

Rejoice, O uncrossed gate!  Rejoice, O wall and protection of those who hasten to thee!  Rejoice, O quiet haven who hast not known wedlock!  O thou who hast given birth in the flesh to thy Creator and God, thou shalt continue to intercede for the sake of those who praise and worship thy birth-giving.

\subsubsection{Kontakion}

Thou didst descend into Hades, my Savior, and shattered its gates, for Thou art almighty. As Creator, Thou didst raise the dead and destroy the sting of death. Thou didst deliver Adam from the curse, O loving One. Therefore, all cry out to Thee: O Lord, save us.

\subsubsection{Hypakoe}

The minds of the ointment-bearing women were dazzled by the angelic scene, and their souls with the divine Resurrection. Wherefore, they spoke to the Apostles, saying, Declare in the nations the Resurrection of the Lord, Who worketh wonders with you, who bestoweth on us the Great Mercy.

\subsection{Tone Six}

\subsubsection{Apolytikion}

When Mary stood at Thy grave, looking for Thy sacred body, angelic powers shone above Thy revered tomb; and the soldiers who were to keep guard became as dead men. Thou led Hades captive and wast not tempted thereby. Thou didst meet the Virgin and didst give life to the world, O Thou, Who art risen from the dead, O Lord, glory to Thee.

\subsubsection{Theotokion}

Thou Who didst call Thy Mother blessed of Thine own good will and didst come to Thy passion shining radiantly upon the Cross, desiring to recall Adam and saying unto the angels: Rejoice with me; for I have found the piece of silver which was lost. O our God, Who with wisdom hast ordered all things, glory to Thee.

\subsubsection{Kontakion}

The Life-giver, Christ our God, raised the dead from the valley of death with His life‑giving hand, awarding Resurrection to all. For, He is the Savior, the Resurrection, the Life and the God of all.

\subsubsection{Hypakoe}

By Thy willing yet life giving Death, O Christ, Thou hast crushed the gates of Hades, because Thou art God, and hast opened the old paradise; and having risen from the dead, Thou hast redeemed our life from corruption.

\subsection{Tone Seven}

\subsubsection{Apolytikion}

Thou didst shatter death by Thy Cross, Thou didst open paradise to the thief; Thou didst turn the sadness of the ointment-bearing women into joy. And didst bid Thine Apostles proclaim a warning, that Thou hast risen O Christ, granting to the world the Great Mercy.

\subsubsection{Theotokion}

In that thou art the treasury of our resurrection O all-praised one, lead thou forth from the pit and bottom of transgression those who set their hope in thee. For thou hast saved those who were guilty of sin, in that thou didst give birth to our Salvation; O thou who before giving birth wast virgin, and at giving birth and after giving birth was virgin still.

\subsubsection{Kontakion}

The power of death no longer rules over us, for Christ hath come destroying and crushing its power. Hades is bound and the prophets together proclaim: The Savior hath appeared saying to the faithful; come forth to the Resurrection.

\subsubsection{Hypakoe}

O Thou Who hast taken our image and our likeness, and endured crucifixion in the flesh, save me by Thy Resurrection, O Christ God, for Thou art the Lover of Mankind.

\subsection{Tone Eight}

\subsubsection{Apolytikion}

From the heights Thou didst descend, O compassionate One, and Thou didst submit to the three-day burial, that Thou might deliver us from passion; Thou art our life and our Resurrection, O Lord, glory to Thee.

\subsubsection{Theotokion}

Thou Who for our sake wast born of a Virgin, and didst suffer crucifixion, O good One, and didst despoil death through death, and as God didst reveal resurrection. Despise not those Whom Thou hast created with Thine own hand, show forth Thy love for mankind, O merciful One. Accept the intercessions of Thy mother, the Theotokos for us, and save Thy despairing people, O our Savior.

\subsubsection{Kontakion}

Rising from the tomb, Thou didst raise the dead and resurrect Adam. Eve rejoices in Thy Resurrection; and the ends of the earth rejoice in Thy rising from the dead, O merciful One.

\subsubsection{Hypakoe}

The ointment-bearing women came to the tomb of the Life-giver, seeking among the dead the Lord Who is not dead; and when they received the glad tidings from the angels, they preached to the Apostles that the Lord hath risen, and granted the world the Great Mercy.

\cleardoublepage
