\section{Third Hour}

\input{prayers/usualBeginning}

\subsection{Psalm 16}

\input{psalms/16}

\subsection{Psalm 24}

\input{psalms/24}

\subsection{Psalm 50}

\input{psalms/50}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

Alleluia, alleluia, alleluia. Glory to thee, O God. \rubric{(thrice)}

Lord, have mercy. \rubric{(thrice)}

\subsection{Troparia and Verses}

\rubric{If it is a weekday of Great Lent, the following troparia and verses are sung in Tone 6, else we say \unrubric{Glory...}, the troparion of the day, then \unrubric{Both now...}. The troparion of the day can be found starting on page \pageref{weekday}.}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\rubric{If it is a weekday of Great Lent, the following troparia and verses are sung in Tone 6, else we say \unrubric{Glory...}, the troparion of the day, then \unrubric{Both now...}}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

O Lord, who at the third hour didst send down upon thine apostles thy Holy Spirit: Take not the same from us, O good One, but renew him in us who pray unto thee. \rubric{(prostration)}

\rubric{Verse 1:} Create in me a clean heart, O God, and renew a right spirit within me. \rubric{(prostration)}

\rubric{Verse 2:} Cast me not away from thy presence, and take not thy Holy Spirit from me. \rubric{(prostration)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

\subsection{Theotokion and Psalm Verses}

O Theotokos, thou art the true vine who didst bud forth for us the Fruit of life. Implore thou him, we beseech thee, O Lady, together with the apostles and all the saints, that he will have mercy on our souls.

Blessed is the Lord God, blessed is the Lord day by day; the God of our salvation shall prosper us along the way. Our God is the God of salvation.

\subsection{Trisagion}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\subsection{Kontakion}

\rubric{The kontakion of the day can be found starting on page \pageref{weekday}. If it is Great Lent, say:}

Blessed art thou, O Christ our God, who hast revealed the fishermen as all-wise by sending down upon them the Holy Spirit; through them thou didst draw the world into thy net. O Lover of mankind, glory to thee.

Glory to the Father, and to the Son, and to the Holy Spirit.

Grant speedy and steadfast consolation unto thy servants, O Jesus, when our spirits are cast down within us. Depart not from our souls in affliction. Be not far from our thoughts in time of trouble, but always defend us. Draw near unto us, draw near unto us, thou who art everywhere present. As thou art ever with thine apostles, so, also, O compassionate One, unite thyself unto those who long for thee, that with one accord we may sing praises unto thee and glorify thine all-holy Spirit.

Both now and ever, and unto ages of ages. Amen.

The hope and protection and refuge of Christians art thou, the impregnable wall and the haven unvexed by storms, O immaculate Theotokos; but in that thou dost save the world by thine unceasing intercessions, call thou us also to remembrance, O all-lauded Virgin.

\rubric{But on Saturday, use \unrubric{Unto thee, O Lord the Author of creation} and on Sunday, use the hypakoe of the proper tone, which can be found starting on page \pageref{resurrectional}.}

\subsection{Prayer of the Hours}

Lord, have mercy. \rubric{(forty times)}

\input{prayers/hours}

Lord have mercy. \rubric{(thrice)}

Glory to the Father, and to the Son, and to the Holy Spirit: both now and ever, and unto ages of ages. Amen.

More honorable than the Cherubim, and more glorious beyond compare than the Seraphim, thou who without stain barest God the Word, and art truly Theotokos, we magnify thee.

\subsection{Prayer of St. Ephraim the Syrian}

\rubric{If it is Great Lent, say the prayer of St. Ephraim the Syrian and the Trisagion.}

\input{prayers/stEphraim}

Holy God... Glory \rubric{and} Both now... All-holy Trinity... Lord, have mercy. \rubric{(3)}... Glory \rubric{and} Both now... Our Father...

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

Lord, have mercy. \rubric{(twelve times)}

\subsection{The Final Prayer}

O Master God, Almighty Father, O Lord, the only-begotten Son Jesus Christ, and O Holy Spirit, one Godhead and one Power: Have mercy on me a sinner; and by the judgments which thou hast established, save me, thine unworthy servant, for thou art blessed unto ages of ages. Amen.

Through the prayers of our holy Fathers, Lord Jesus Christ our God, have mercy on us and save us. Amen.

\cleardoublepage
